---
title: "ER2 Kagera Data Analysis 1"
author: "Elyse St Sauver"
date: "2025-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse, stargazer, ggplot2, sandwich, fastDummies, lmtest, scales, knitr, kableExtra, DT, fixest, modelsummary)
```

# Initial Data Cleaning

Notes for Mira: \\
  - The [COMPLETE] tag means the task is fully done. \\
  - Three asterisks (***) mean this is a note to bring up with Henry and/or the enumerators. \\
  - The [To-Do] tag means the task is still incomplete. \\
  
  ____________________________________________________________________________________________________________________________________________________

  Let's import the data and check for abnormalities. More specifically, we're importing the data and looking for odd patterns like: \\ 
  - NA values where there should be something else (like a 0 or a "False") \\
  - Columns where every/nearly every participant responded the same \\
  - Variables out of order \\
  - Columns that need reformatting (ex. "1 - Least satisfied" and "2" in the same column, or "1 2 3 0 9" which should be one column each for "1" "2", etc.) \\
  - Anything else that looks unusual or wrong \\
  
  Some NA values are fine, we're just especially concerned with those in columns where we need to do analysis. Those include the DCE responses*, 3-study method questions (Haushofer, etc), the activity response section, and the demographics. To start, take a look at the data and see if anything looks weird to you, I've typed up my initial thoughts below. When I figured something out while working with the data, I indicate it below as well. \\
  
  *You might notice the returningresults_merged dataset doesn't have the DCE data. For some reason, it's separate in SurveyCTO-- that's okay, we just have to join the datasets together. To begin with, look at the datasets separately and we'll join them in a later step. \\
  

```{r Non-DCE Data Import}
kageradata <- read.csv("returningresults_merged.csv")
```

Data Notes: 
  - ID indicator is respondentID or respondent_index
  - For joining with DCE data, join column is SET.OF.dce_game

Data Issues:
  - [COMPLETE][No code needed] what is respo_confirm? 
          Answer --> Some respondents did not confirm and are replaced 
  - *** part_study_1, who_participated --> not complete
  - *** contact_research --> not complete ("Did you get contact information for researchers"? Confirm what this question is)
  - *** clear_plans, ask_results --> almost empty
  
  - [COMPLETE][No code needed] keep_documentation/have_documentation might be in the wrong order (Confirm order)
          Answer --> Nope, this is fine. It goes "Did they give you a written document to keep" > "Did you keep that document after the interview" > "Do you still have it"
  - [COMPLETE][Data Cleaning] num_past_studies has NAs that Should be 0 (when past_study_participation is 0) 
  
  - *** many 0s for past_study_participation, so much of the activity response section is empty
  - *** future_study_willingness --> not complete
  
  
```{r DCE Data Import}
dcedata <- read.csv("dce_returningresults_merged.csv")
scenarios <- read.csv("scenario_dataset.csv")
```

DCE Data Notes:
    - No ID indicator, for joining with Kagera data, join column is SET.OF.dce_game
    - DCE data has 10 observations per ID, so it will be a many-to-one join (and that's okay)
    
DCE Issues: 
    - [COMPLETE][Join Sets] Need to parse the game_matrix (stitched_output_##.jpg) to the actual levels and features from the Excel sheet. This means another join
    - [COMPLETE][Join Sets] Join on the game_matrix column (to the "image" column in the Excel spreadsheet of DCE features and levels)

# To-Do for Both Datasets: \\

  Each section below is organized to address one of these points. Oustanding tasks (to-dos) are tagged with that in the section heading

  - [COMPLETE][Data Cleaning] Resolve items in Issues sections
  - [COMPLETE][Data cleaning] Distribute rank_results_methods to their own columns
  - [COMPLETE][Data cleaning] Current rank_results_methods_1, rank_results_methods_2 are useless, replace with rank *of* results method 1, etc
  - [COMPLETE][Data cleaning] Distribute first_position, second_position, third_position to "first_study", "first_method", "second study", etc.
  - [COMPLETE][Data cleaning] Distribute rank_results_preference to Study 1 Rank column, Study 2 Rank column, etc. 
      - [COMPLETE][Data cleaning] Do the same for rank_formats_preference and rank_formats_clarity
  - [COMPLETE][Join Sets] Join DCE data with levels/features sheet
  - [COMPLETE][Join Sets] Join DCE data post-merge with levels/featuers to the kagera data, and clean
  - [COMPLETE][Analyze DCE Data] Analyze DCE data
      - [COMPLETE][Analyze DCE Data: Linear Regression] Regress likelihood of choosing A when each feature level is present in A, present in B. 
      - [COMPLETE][Analyze DCE Data: DCE Graph...] Create graph of likelihood of choosing A/B given compensation level of A/B. 
  - [To-Do] Analyze three study experiment (especially the "likelihood" variables)
  - [To-Do] Can we do anything with the activity data? It's very incomplete, but let's try...
  - [To-Do] Summarize comment variables (exercise_comment and exercise_comment_oth for DCE comments, end_commet for overall comments)
  - [COMPLETE][Summary Statistics Table] Create a table of summary statistics for each variable 
  - [To-Do][Summary Statistics Table] Make variables categorical/numerical as appropriate
  - [To-Do] Analyze the rank results methods 1-9 (What are the top method preferences?)
  - [To-Do] Summarize challenges participants identified

```{r Join Sets}
# Augment the DCE dataset with the scenarios set
  # Check for respondent index and image label presence, then join on those variables

  scenarios <- select(scenarios, -c(respondent_ID, choicenumber, choicenumber2,
                                    participants_title.A, participants_title.B,
                                    community_title.A, community_title.B,
                                    policymakers_title.A, policymakers_title.B,
                                    compensation_title.A, compensation_title.B,
                                    researchfunding_title.A, researchfunding_title.B))
  
  dcedata |> 
    filter(is.na(SET.OF.dce_game) | is.na(game_matrix))
  
  kageradata |> 
    filter(is.na(SET.OF.dce_game))
  
  scenarios |>
    filter(is.na(image))

  # Augment the DCE dataset with the scenarios dataset (so that we have a column with each feature's level for A and B)
  dcedata_aug <- left_join(dcedata, scenarios, by = join_by(game_matrix == image), suffix = c(".Collected", ".Generated"))

  # Join the augmented DCE dataset to the Kagera data
  fulldata <- left_join(dcedata_aug, kageradata, by = c("SET.OF.dce_game"))
```

```{r Data Cleaning}
# Cleaning the main Kagera dataset first. 

  # Some respondants did not confirm, so they have been replaced with other respondants. Dropping the nonresponding rows. 
fulldata <- subset(fulldata, respo_confirm == 1)

  # num_past_studies has NAs that should be 0 when past_study_participation is 0
fulldata$num_past_studies[is.na(fulldata$num_past_studies) & fulldata$past_study_participation == 0] <- 0

# Rank varaiables --> columns for radio, sms, etc. and cell values are the rank designated by participant
  # Some of the columns have collections of data that should be distributed into individual columns. These are resolved here. 
  # rank_results_methods
  # first_position, second_position, third_position
  # rank_results_preference
  # rank_formats_preference
  # rank_formats_clarity
max_splits <- max(sapply(strsplit(fulldata$rank_results_methods, " "), length)) # Determine max splits
fulldata <- fulldata %>%
  tidyr::separate(rank_results_methods, into = paste0("rank_results_methods_", 1:max_splits), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_results_preference, into = paste0("rank_results_preference_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_formats_preference, into = paste0("rank_formats_preference_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_formats_clarity, into = paste0("rank_formats_clarity_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  #Now separate out study title and method
  tidyr::separate(first_position, into = c("first_study", "first_method"), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(second_position, into = c("second_study", "second_method"), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(third_position, into = c("third_study", "third_method"), sep = " ", convert = TRUE, fill = "right")


# The following section provides code to fix a miscoding where satisfaction scales show mixed numerical and string output, but this was fixed after the pilot. 

# fulldata <- fulldata %>%
#   mutate(across(77:85, ~ case_when(
#     . == "not satisfied" ~ as.character(1),
#     . == "very satisfied" ~ as.character(5),
#     TRUE ~ as.character(.)
#   )),
#   across(45, ~ case_when(
#     . == "Not busy at all" ~ as.character(1),
#     . == "Very busy" ~ as.character(5),
#     TRUE ~ as.character(.)
#   )),
#   across(88, ~ case_when(
#     . == "Least interested" ~ as.character(1),
#     . == "Most interested" ~ as.character(5),
#     TRUE ~ as.character(.)
#   )))

# Generate dummy var for study, position, method
threestudy_analysis <- select(fulldata, c("respondentID", 245:259))

threestudy_analysis <- threestudy_analysis %>%
  pivot_longer(cols = c("first_study", "first_method", "second_study", "second_method", "third_study", "third_method"),
               names_to = c("order", ".value"),
               names_sep = "_") %>%
  mutate(order = factor(order, levels = c("first", "second", "third")))

threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_results_preference_1", "rank_results_preference_2", "rank_results_preference_3"))
threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_formats_preference_1", "rank_formats_preference_2", "rank_formats_preference_3"))
threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_formats_clarity_1", "rank_formats_clarity_2", "rank_formats_clarity_3"))
threestudy_analysis$results_preference_ranking <- NA
threestudy_analysis$formats_preference_ranking <- NA
threestudy_analysis$formats_clarity_ranking <- NA
#Repeat for formats preference, formats clarity
j = 1

while(j <= nrow(threestudy_analysis)) {
    current_row <- threestudy_analysis[j,]
    order_num = case_when(
      current_row$order == "first" ~ 1,
      current_row$order == "second" ~ 2,
      current_row$order == "third" ~ 3
    )
    results_preference_ranking = case_when(
      order_num == 1 & current_row$rank_results_preference_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_results_preference_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_results_preference_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_results_preference_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_results_preference_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_results_preference_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_results_preference_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_results_preference_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_results_preference_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "results_preference_ranking"] <- results_preference_ranking
    formats_preference_ranking = case_when(
      #order_num == 1 & current_row$rank_formats_preference_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_formats_preference_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_formats_preference_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_formats_preference_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_formats_preference_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_formats_preference_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_formats_preference_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_formats_preference_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_formats_preference_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "formats_preference_ranking"] <- formats_preference_ranking
    formats_clarity_ranking = case_when(
      order_num == 1 & current_row$rank_formats_clarity_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_formats_clarity_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_formats_clarity_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_formats_clarity_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_formats_clarity_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_formats_clarity_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_formats_clarity_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_formats_clarity_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_formats_clarity_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "formats_clarity_ranking"] <- formats_clarity_ranking
    j <- j + 1
}

threestudy_long <- unique(select(threestudy_analysis, c("respondentID", "order", "study", "method", "results_preference_ranking", "formats_preference_ranking", "formats_clarity_ranking")))



#Add columns for each of 5 features, levels, for each A and B (1 if present, 0 else)
features <- colnames(dcedata_aug)[9:19]
features <- features[features != "compset"]
dceanalysis <- dummy_cols(dcedata_aug, select_columns = features)

#If feature is the same in A and B, make 0. For continuous variables, use delta

#Force shared feature levels across A and B equal to 0
dceanalysis <- dceanalysis %>%
  rowwise() %>%
  mutate(across(starts_with("participants_image.A_") | starts_with("participants_image.B_"), 
                ~ if_else(participants_image.A == participants_image.B, as(0, class(.)), .)),
         across(starts_with("community_image.A_") | starts_with("community_image.B_"), 
                ~ if_else(community_image.A == community_image.B, as(0, class(.)), .)),
         across(starts_with("policymakers_image.A_") | starts_with("policymakers_image.B_"), 
                ~ if_else(policymakers_image.A == policymakers_image.B, as(0, class(.)), .)),
         across(starts_with("compensation_image.A_") | starts_with("compensation_image.B_"), 
                ~ if_else(compensation_image.A == compensation_image.B, as(0, class(.)), .)),
         across(starts_with("researchfunding_image.A_") | starts_with("researchfunding_image.B_"), 
                ~ if_else(researchfunding_image.A == researchfunding_image.B, as(0, class(.)), .))) %>%
  ungroup()

dceanalysis <- dceanalysis %>%
  rename(option_selected = dce_potion)

#Create comp_delta and funding_delta for continuous features
dceanalysis$comp_delta <- NA
dceanalysis$funding_delta <- NA
i = 1

while(i <= nrow(dceanalysis)) {
    current_row <- dceanalysis[i,]
    compA <- 0
    compB <- 0
    fundingA <- 0
    fundingB <- 0
    compA = case_when(
      current_row$compensation_image.A_0Tsh.jpeg == 1 ~ 0,
      current_row$compensation_image.A_1Tsh.jpeg == 1 ~ 1,
      current_row$compensation_image.A_2Tsh.jpeg == 1 ~ 2,
      current_row$compensation_image.A_3Tsh.jpeg == 1 ~ 3,
      current_row$compensation_image.A_4Tsh.jpeg == 1 ~ 4,
      current_row$compensation_image.A_5Tsh.jpeg == 1 ~ 5,
      current_row$compensation_image.A_6Tsh.jpeg == 1 ~ 6,
      current_row$compensation_image.A_7Tsh.jpeg == 1 ~ 7,
      current_row$compensation_image.A_8Tsh.jpeg == 1 ~ 8,
      current_row$compensation_image.A_9Tsh.jpeg == 1 ~ 9,
      current_row$compensation_image.A_10Tsh.jpeg == 1 ~ 10
    )
    compB = case_when(
      current_row$compensation_image.B_0Tsh.jpeg == 1 ~ 0,
      current_row$compensation_image.B_1Tsh.jpeg == 1 ~ 1,
      current_row$compensation_image.B_2Tsh.jpeg == 1 ~ 2,
      current_row$compensation_image.B_3Tsh.jpeg == 1 ~ 3,
      current_row$compensation_image.B_4Tsh.jpeg == 1 ~ 4,
      current_row$compensation_image.B_5Tsh.jpeg == 1 ~ 5,
      current_row$compensation_image.B_6Tsh.jpeg == 1 ~ 6,
      current_row$compensation_image.B_7Tsh.jpeg == 1 ~ 7,
      current_row$compensation_image.B_8Tsh.jpeg == 1 ~ 8,
      current_row$compensation_image.B_9Tsh.jpeg == 1 ~ 9,
      current_row$compensation_image.B_10Tsh.jpeg == 1 ~ 10
    )
    fundingA = case_when(
      current_row$researchfunding_image.A_research0.jpeg == 1 ~ 0,
      current_row$researchfunding_image.A_research2.jpeg == 1 ~ 2,
      current_row$researchfunding_image.A_research4.jpeg == 1 ~ 4,
      current_row$researchfunding_image.A_research6.jpeg == 1 ~ 6,
      current_row$researchfunding_image.A_research8.jpeg == 1 ~ 8,
      current_row$researchfunding_image.A_research10.jpeg == 1 ~ 10,
      current_row$researchfunding_image.A_research12.jpeg == 1 ~ 12,
      current_row$researchfunding_image.A_research14.jpeg == 1 ~ 14,
      current_row$researchfunding_image.A_research16.jpeg == 1 ~ 16,
      current_row$researchfunding_image.A_research18.jpeg == 1 ~ 18,
      current_row$researchfunding_image.A_research20.jpeg == 1 ~ 20,
      .default = 0
    )
    fundingB = case_when(
      current_row$researchfunding_image.B_research0.jpeg == 1 ~ 0,
      current_row$researchfunding_image.B_research2.jpeg == 1 ~ 2,
      current_row$researchfunding_image.B_research4.jpeg == 1 ~ 4,
      current_row$researchfunding_image.B_research6.jpeg == 1 ~ 6,
      current_row$researchfunding_image.B_research8.jpeg == 1 ~ 8,
      current_row$researchfunding_image.B_research10.jpeg == 1 ~ 10,
      current_row$researchfunding_image.B_research12.jpeg == 1 ~ 12,
      current_row$researchfunding_image.B_research14.jpeg == 1 ~ 14,
      current_row$researchfunding_image.B_research16.jpeg == 1 ~ 16,
      current_row$researchfunding_image.B_research18.jpeg == 1 ~ 18,
      current_row$researchfunding_image.B_research20.jpeg == 1 ~ 20,
      .default = 0
    )
    #Check if any comp or research funding dummy variables are == 1
    #For nonzero variables, case_when assign numerical value
    #Assign comp_delta, comp_funding equal to the differences (A - B, not absolute value since positive/negative indicates whether A or B is greater)
    comp_delta_value <- compA[i] - compB[i]
    funding_delta_value <- fundingA[i] - fundingB[i]
  
        # Check for NA and replace with 0 if NA
    dceanalysis[i, "comp_delta"] <- ifelse(is.na(comp_delta_value), 0, comp_delta_value)
    dceanalysis[i, "funding_delta"] <- ifelse(is.na(funding_delta_value), 0, funding_delta_value)
    
    i <- i + 1
}

```

```{r Summary Statistics Table: Create the table}

# We basically want summary statistics for every var and a table with everything labeled clearly. Ideally have the question on the left, stats on the right.
#   - If numerical: Median, mean, range, standard deviation of responses for numerical
#   - If categorical: Tabulation (Count of each response type)
#   - For everything, we want a number of responses (N) and response rate (%)

# The part left to do is to finish the pretty variable name correspondence

summary_subset <- select(fulldata, c(
"location",
"participants_image.A",
"community_image.A",
"policymakers_image.A",
"compensation_image.A",
"researchfunding_image.A",
"participants_image.B",
"community_image.B",
"policymakers_image.B",
"compensation_image.B",
"researchfunding_image.B",
"duration",
"consent",
"resp_age",
"resp_gender",
"resp_marital",
"hh_adults",
"hh_children",
"hh_teen",
"resp_education",
"work_seven_days",
"work_three_month",
"resp_busy",
"remember_study",
"hear_study",
"enrol_study",
"receive_result",
"explain_study",
"understand_study",
"study_documentation",
"keep_documentation",
"have_documentation",
"researchers_names",
"contact_research",
"informed_consent",
"informed_study_results",
"clear_plans",
"ask_results",
"satisfied_compensation",
"satisfied_time",
"satisfied_interaction",
"satisfied_information",
"info_received_during_study",
"info_received_end_study",
"clarity_timelines",
"relevance_personal",
"relevance_community",
"lasting_impacts",
"lasting_impacts_description",
"future_participation_interest",
"challenges_encountered",
"challenges_description_oth2",
"challenges_resolution",
"past_study_participation",
"num_past_studies",
"studies_returned_info",
"audio_results_received",
"audio_message_listened",
"audio_results_understandable",
"sms_results_received",
"sms_message_read",
"sms_results_understandable",
"website_results_received",
"website_link_clicked",
"website_results_understandable",
"flyer_results_received",
"flyer_read",
"flyer_results_understandable",
"posted_flyer_results_received",
"posted_flyer_read",
"posted_flyer_results_understandable",
"social_media_results_seen",
"social_media_interacted",
"social_media_results_understandable",
"video_results_received",
"video_watched",
"video_results_understandable",
"public_meeting_invited",
"public_meeting_attended",
"public_meeting_results_understandable",
"private_meeting_invited",
"private_meeting_attended",
"private_meeting_results_understandable",
"phone_call_results_heard",
"phone_call_answered",
"phone_call_results_understandable",
"other_results_received",
"other_results_understandable",
"results_wait_time_perception",
"results_return_time_satisfaction",
"future_study_willingness",
"important_to_return_results_resources",
"returning_results_shows_respect",
"participants_right_to_results",
"importance_of_results_returned",
"preferred_results_return_method",
"study_participants",
"non_participants_research_communities",
"local_community_leaders",
"local_government_officials",
"foreign_government_officials",
"religious_leaders",
"other_researchers",
"result_timeline",
"likelihood_watch_video_results",
"likelihood_read_sms_results",
"likelihood_listen_audio_results",
"read_sms",
"understood_exercise",
"exercise_comment",
"exercise_comment_oth",
"own_mobile_phone",
"own_smartphone",
"received_messages_30days",
"interested_receive_result",
"connected_smartphone",
"interview_result",
))

pretty_names <- c(
location = "Location",
participants_image.A = "A - Participant",
community_image.A = "A - Community",
policymakers_image.A = "A - Policymakers",
compensation_image.A = "A - Compensation",
researchfunding_image.A = "A - Research Funding",
participants_image.B = "B - Participant",
community_image.B = "B - Community",
policymakers_image.B = "B - Policymakers",
compensation_image.B = "B - Compensation",
researchfunding_image.B = "B - Research Funding",
duration = "Duration",
consent = "Do you consent to participate?",
resp_age = "Respondent Age",
resp_gender = "Respondent Gender",
resp_marital = "Respondent Marital Status",
hh_adults = "How many adults over the age of 18, other than you live in your household?",
hh_children = "How many children age 0-6 live in your household?",
hh_teen = "How many children age 7-17 live in your household?",
resp_education = "Highest level of education",
work_seven_days = "In the past seven days, have you spent any time engaged in paid economic activies (i.e., work?)",
work_three_month = "In the past three months, have you spent any time engaged in paid economic activies (i.e., work?)",
resp_busy = "This question won't affect the timing or length of the survey. On a scale of 1-5, how busy would you say the rest of your day is?",
remember_study = "Do you or any other household member remember being part of this study?",
hear_study = "How did you first hear about the study?",
enrol_study = "What was your primary reason for enrolling in the study?",
receive_result = "Did you expect to recieve results when you enrolled in the study?",
explain_study = "The first time you met the interviewer, did they explain to you what the objectives of the study were?",
understand_study = "Did you understand what the study was about from their description?",
study_documentation = "Did the interviewer give you a written document with information about the study for you to keep?",
keep_documentation = "Did you keep the document after the initial interview?",
have_documentation = "Do you still have [the documentation you were given]?",

# Where is the question about risks/benefits? Missing 10a/b and 11a/b.

researchers_names = "Were you given names of researchers that you could contact if you ever run into a problem with your involvement in the study?",
contact_research = "Did you ever try to contact [the researchers]?",
informed_consent = "Were you given the option to not participate in the study?", 
          #Is that what this question corresponds to...?
informed_study_results = "Were you informed of plans to return results directly to participants at the conclusion of the study?",
clear_plans = "Were these plans [to return results] made clear to you?",
ask_results = "Did you ask if results would be returned?",
#interviewer_interaction,
          #This question corresponds to one of "How many times did you meet with interviewers to answer questions for this study?" and "How would you describe your interactions with the interviewer during your interviews for the study? Positve, somewhat positive, netural, somewhat negative, negative?"

# activity_1,
# activity_1b,
# activity_2,
# activity_2b,
# activity_3,
# activity_3b,
# activity_4,
# activity_4b,
# activity_5,
# activity_5b,
# activity_6,
# activity_6b,


 satisfied_compensation = "How satisfied are you with the compensation received for participating?",
 satisfied_time = "How satisfied are you with the amount of time spent participating in the research?",
 satisfied_interaction = "How satisfied are you with the interactions with interviewers?",
 satisfied_information = "How satisfied are you with the amount of relevant information you received when deciding to participate?",
 info_received_during_study = "How satisfied are you with the amount of relevant information received during the study?",
 info_received_end_study = "How satisfied are you with the amount of relevant information received when the study ended?",
 clarity_timelines = "How satisfied are you with the clarity about timelines (start and end dates of study)?",
 relevance_personal = "How satisfied are you with the relevance of the research to you personally?",
 relevance_community = "How satisfied are you with the relevance of the research to your community?",
 lasting_impacts = "Did you see any lasting impacts of the study?",
 lasting_impacts_description = "What were [the lasting impacts?]",
 future_participation_interest = "How interested would you be to participate if there was a similar study in the future?",
 challenges_encountered = "Did you or others in the study run into challenges with your involvement in the study?",
 challenges_description_oth2 = "If yes, can you describe the challenge?",
 challenges_resolution = "How was the challenge resolved?",
 past_study_participation = "Did you or any other member of your household participate in other projects that fill this definition of a research study in the past 5 years?",
 num_past_studies = "If yes, how many studies, excluding the one we just talked about?",
# study_activities,
# study_activities_1,
# study_activities_2,
# study_activities_3,
# study_activities_4,
# study_activities_5,
# study_activities_6,
# study_activities_7,
# study_activities_8,
# study_activities_9,
# study_activities_10,
# study_activities_11,
# study_activities_12,
# study_activities_13,
# study_activities_oth,

 studies_returned_info = "How many of these other research studies returned information to you?",
 audio_results_received = "Did you recieve results through an audio message?",
 audio_message_listened = "Did you listen to the audio message?",
 audio_results_understandable = "For you personally, were the results understandable?",
 sms_results_received = "Did you recieve results through an SMS?",
 sms_message_read = "Did you read the SMS?",
 sms_results_understandable = "For you personally, were the results understandable?",
 website_results_received = "Did you receive results through a link to a website?",
 website_link_clicked = "Did you click through the website?",
 website_results_understandable = "For you personally, were the results understandable?",
 flyer_results_received = "Did you recieve results through a flyer?",
 flyer_read = "Did you read the flyer?",
 flyer_results_understandable = "For you personally, were the results understandable?",
 posted_flyer_results_received = "Did you receive results through a publicly posted flyer on a community board?",
 posted_flyer_read = "Did you read the posted flyer?",
 posted_flyer_results_understandable = "For you personally, were the results understandable?",
 social_media_results_seen = "Did you see results shared on a social media post?",
 social_media_interacted = "Did you interact with the social media post?",
 social_media_results_understandable = "For you personally, were the results understandable?",
 video_results_received = "Did you recieve results through a video?",
 video_watched = "Did you watch the video?",
 video_results_understandable = "For you personally, were the results understandable?",
 public_meeting_invited = "Were you invited to hear about the results at a public meeting?",
 public_meeting_attended = "Did you attend the public meeting?",
 public_meeting_results_understandable = "For you personally, were the results understandable?",
 private_meeting_invited = "Were you invited to hear about the results at a private meeting?",
 private_meeting_attended = "Did you attend the private meeting?",
 private_meeting_results_understandable = "For you personally, were the results understandable?",
 phone_call_results_heard = "Did you hear about the results through a phone call?",
 phone_call_answered = "Did you answer the phone call?",
 phone_call_results_understandable = "For you personally, were the results understandable?",
 other_results_received = "Did you recieve results in any other form not listed?",
 #other_results_received_oth = "",
 other_results_understandable = "For you personally, were the results understandable?",
 results_wait_time_perception = "[Considering the last time results were returned to you] did this time waiting for results seem short, long, or as expected to you? ",
 results_return_time_satisfaction = "Were you satisfied with how long it took for results to be returned to you?",
 future_study_willingness = "Has your past experience with research studies made you more or less willing to participate in future studies?",
# past_study_challenges_details,
# past_study_challenges_addressed_by,
# past_study_challenges_addressed_by_1,
# past_study_challenges_addressed_by_2,
# past_study_challenges_addressed_by_3,
# past_study_challenges_addressed_by_4,
# past_study_challenges_addressed_by_5,
# past_study_challenges_addressed_by_6,
# past_study_challenges_addressed_by_7,
# past_study_challenges_addressed_by_8,
# past_study_challenges_addressed_by_9,
# past_study_challenges_addressed_by_10,
# past_study_challenges_addressed_by_oth,
# other_participant_challenges_heard,
# other_participant_challenges_heard_1,
# other_participant_challenges_heard_2,
# other_participant_challenges_heard_3,
# other_participant_challenges_heard_4,
# other_participant_challenges_heard_5,
# other_participant_challenges_heard_6,
# other_participant_challenges_heard_7,
# other_participant_challenges_heard_8,
# other_participant_challenges_heard_9,
# other_participant_challenges_heard_10,
# other_participant_challenges_heard_oth,
# other_participant_challenges_details,
# other_participant_challenges_addressed_by,
# other_participant_challenges_addressed_by_1,
# other_participant_challenges_addressed_by_2,
# other_participant_challenges_addressed_by_3,
# other_participant_challenges_addressed_by_4,
# other_participant_challenges_addressed_by_5,
# other_participant_challenges_addressed_by_6,
# other_participant_challenges_addressed_by_7,
# other_participant_challenges_addressed_by_8,
# other_participant_challenges_addressed_by_9,
# other_participant_challenges_addressed_by_10,
# who_involved,
# who_involved_1,
# who_involved_2,
# who_involved_3,
# who_involved_4,
# who_involved_5,
# who_involved_6,
# who_involved_7,
# who_involved_8,
# who_involved_9,
# who_involved_10,
 important_to_return_results_resources = "Do you agree/disagree that it is important for researchers to spend resources, such as time and money, to return research results to participants like yourself and other people in this community?",
 returning_results_shows_respect = "Do you agree/disagree that returning research results to participants/community is the way for researchers to show respect to the community",
 participants_right_to_results = "Do you agree/disagree that participants have a right to be given the results of research they participated in.",
 importance_of_results_returned = "When deciding to participate in a research study, how important is it that results are returned to you at the end of the study?",
 preferred_results_return_method = "In general, what would you prefer of these four choices:

1. Receive results one time at the conclusion of the study
2. Receive updates in the middle and results at the end of the study
3. Receive multiple update throughout the study and results at the end
4. Do not receive any updates or results.",
 study_participants = "Should results of this study be shared with study participants",
 non_participants_research_communities = "Should results of this study be shared with non-participants in participant communities",
 local_community_leaders = "Should results of this study be shared with local community leaders",
 local_government_officials = "Should results of this study be shared with local governmental officials",
 foreign_government_officials = "Should results of this study be shared with foreign governmental officials",
 religious_leaders = "Should results of this study be shared with religious leaders",
 other_researchers = "Should results of this study be shared with other researchers",
 result_timeline = "In the event that results for this study are shared with you, what is your expected timeline for receiving them?",
# rank_results_methods_1,
# rank_results_methods_2,
# rank_results_methods_3,
# rank_results_methods_4,
# rank_results_methods_5,
# rank_results_methods_6,
# rank_results_methods_7,
# rank_results_methods_8,
# rank_results_methods_9,
# first_study,
# first_method,
# second_study,
# second_method,
# third_study,
# third_method,
# rank_results_preference_1,
# rank_results_preference_2,
# rank_results_preference_3,
# rank_formats_preference_1,
# rank_formats_preference_2,
# rank_formats_preference_3,
# rank_formats_clarity_1,
# rank_formats_clarity_2,
# rank_formats_clarity_3,
 likelihood_watch_video_results = "How likely are you to spend your own time and data to watch video results for the study you are currently a participant of?",
 likelihood_read_sms_results = "How likely are you to spend your own time and data to read SMS results for the study you are currently a participant of?",
 likelihood_listen_audio_results = "How likely are you to spend your own time and data to listen to audio results for the study you are currently a participant of?",
 read_sms = "[ENUMERATOR]: did you read out loud the SMS messages, or did the participant read it individually/independently?",
 #game_size,
 #dce_game_count,
 understood_exercise = "[ENUMERATOR]: Do you think the respondent understood the exercise? ",
 exercise_comment = "[ENUMERATOR]: Do you think the respondent paid attention to the choices in front of him/her?",
 exercise_comment_oth = "[ENUMERATOR]: Does the respondent appear to have enjoyed the exercise?",
 own_mobile_phone = "Do you currently own a mobile phone?",
 own_smartphone = "Is it a smartphone?",
 received_messages_30days = "In the past 30 days, did you receive any messages in your phone?",
 interested_receive_result = "Are you interested in receiving the results of this study? Please bear in mind that researchers may take a long time to complete the study and get the results.",
 connected_smartphone = "Is this number connected to a smartphone or regular phone?",
 interview_result = "[ENUMERATOR]: PLEASE TAKE A FEW MOMENTS TO COMMENT ON THE INTERVIEW."
 )


# Separate variables by type
categorical_vars <- summary_subset %>% select(where(~ is.character(.) | is.factor(.)))
numeric_vars <- summary_subset %>% select(where(is.numeric))

# Categorical Summary
cat_summary <- map_df(names(categorical_vars), function(var) {
  var_data <- summary_subset[[var]]
  tab <- table(var_data, useNA = "ifany")
  response_rate <- sum(!is.na(var_data)) / length(var_data)
  tibble(
    Variable = var,
    N_Responses = sum(!is.na(var_data)),
    Missing = sum(is.na(var_data)),
    Response_Rate = percent(response_rate, accuracy = 0.1),
    Response_Summary = str_wrap(paste(names(tab), tab, sep = " = ", collapse = "; "), width = 80)
  )
})

# Numeric Summary
num_summary <- map_df(names(numeric_vars), function(var) {
  var_data <- summary_subset[[var]]
  tibble(
    Variable = var,
    N_Responses = sum(!is.na(var_data)),
    Missing = sum(is.na(var_data)),
    Response_Rate = percent(sum(!is.na(var_data)) / length(var_data), accuracy = 0.1),
    Mean = round(mean(var_data, na.rm = TRUE), 2),
    Median = round(median(var_data, na.rm = TRUE), 2),
    SD = round(sd(var_data, na.rm = TRUE), 2),
    Range = paste0(round(min(var_data, na.rm = TRUE), 2), " - ", round(max(var_data, na.rm = TRUE), 2))
  )
})

# Use the pretty names
cat_summary <- cat_summary %>%
  mutate(Variable = ifelse(Variable %in% names(pretty_names), pretty_names[Variable], Variable))
num_summary <- num_summary %>%
  mutate(Variable = ifelse(Variable %in% names(pretty_names), pretty_names[Variable], Variable))


# View: Interactive tables
datatable(cat_summary, 
          caption = "Summary of Categorical Variables",
          options = list(pageLength = 10, scrollX = TRUE))

datatable(num_summary,
          caption = "Summary of Numeric Variables",
          options = list(pageLength = 10, scrollX = TRUE))

# 
# # Alternate View: Pretty kable tables
# print("Categorical Summary")
# cat_summary %>%
#   arrange(Variable) %>%
#   kable("html", escape = FALSE, caption = "Summary of Categorical Variables") %>%
#   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
# 
# print("Numeric Summary")
# num_summary %>%
#   arrange(Variable) %>%
#   kable("html", escape = FALSE, caption = "Summary of Numeric Variables") %>%
#   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
# 
# 
```

```{r Analyze DCE data: Linear Regression}

#- Regress likelihood of choosing A when each feature level is present in A, present in B. 
## DCE Linear Regression Analysis

# This regression analysis regressed the option selected (A = 1, B = 0) on the presence of the various features and levels therein. Results are presented with robust standard errors and clustered at the respondent level unless otherwise specified.


na_summary <- colSums(is.na(dceanalysis))

# Filter to show only columns with at least one NA
na_summary[na_summary > 0]

# Create a named vector for variable labels
var_labels <- c(
  "participants_image.A_participant1.jpeg" = "A - No results returned to participants",
  "participants_image.A_participant2.jpeg" = "A - Results returned remotely to participants",
  "participants_image.A_participant3.jpeg" = "A - Results returned in person to participants",
  "community_image.A_community1.jpeg" = "A - No results returned to community",
  "community_image.A_community2.jpeg" = "A - Results returned remotely to c. leader",
  "community_image.A_community3.jpeg" = "A - Results returned in person to community",
  "policymakers_image.A_policy1.jpeg" = "A - No results returned to policymakers",
  "policymakers_image.A_policy2.jpeg" = "A - Report to policymakers",
  "policymakers_image.A_policy3.jpeg" = "A - Half-day policymaker workshop",
  "participants_image.B_participant1.jpeg" = "B - No results returned to participants",
  "participants_image.B_participant2.jpeg" = "B - Results returned remotely to participants",
  "participants_image.B_participant3.jpeg" = "B - Results returned in person to participants",
  "community_image.B_community1.jpeg" = "B - No results returned to community",
  "community_image.B_community2.jpeg" = "B - Results returned remotely to c. leader",
  "community_image.B_community3.jpeg" = "B - Results returned in person to community",
  "policymakers_image.B_policy1.jpeg" = "B - No results returned to policymakers",
  "policymakers_image.B_policy2.jpeg" = "B - Report to policymakers",
  "policymakers_image.B_policy3.jpeg" = "B - Half-day policymaker workshop",
  "comp_delta" = "Compensation Difference",
  "funding_delta" = "Funding Difference",
  "game_index" = "Game Number (1st, 2nd, etc)",
  "SET.OF.dce_game" = "Fixed Effect (Respondent)"
)

# Fit the model with fixed effects
dce_model <- feols(
  option_selected ~ 
    participants_image.A_participant1.jpeg +
    participants_image.A_participant2.jpeg +
    participants_image.A_participant3.jpeg +
    community_image.A_community1.jpeg +
    community_image.A_community2.jpeg +
    community_image.A_community3.jpeg +
    policymakers_image.A_policy1.jpeg +
    policymakers_image.A_policy2.jpeg +
    policymakers_image.A_policy3.jpeg +
    participants_image.B_participant1.jpeg +
    participants_image.B_participant2.jpeg +
    participants_image.B_participant3.jpeg +
    community_image.B_community1.jpeg +
    community_image.B_community2.jpeg +
    community_image.B_community3.jpeg +
    policymakers_image.B_policy1.jpeg +
    policymakers_image.B_policy2.jpeg +
    policymakers_image.B_policy3.jpeg +
    comp_delta +
    funding_delta +
    game_index | 
    SET.OF.dce_game,  # This is your fixed effect
  data = dceanalysis,
  cluster = ~SET.OF.dce_game  # Clustered standard errors (robust to within-respondent correlation)
)

# Display results nicely with custom labels
modelsummary(dce_model, stars = TRUE, gof_omit = 'IC|Log|Adj|FE', 
             coef_map = var_labels)


```

```{r Analyze DCE data: DCE Graph of chioce given comp level}

#- Create graph of likelihood of choosing A/B given compensation level of A/B. 
dce_compensation_dataset <- select(dceanalysis, c("option_selected", "compensation_image.A", "compensation_image.B")) %>%
  
  # Create compA and compB columns based on which image column is 1
  mutate(
    compA = case_when(
      compensation_image.A == "0Tsh.jpeg" ~ 0,
      compensation_image.A == "1Tsh.jpeg" ~ 1,
      compensation_image.A == "2Tsh.jpeg" ~ 2,
      compensation_image.A == "3Tsh.jpeg" ~ 3,
      compensation_image.A == "4Tsh.jpeg" ~ 4,
      compensation_image.A == "5Tsh.jpeg" ~ 5,
      compensation_image.A == "6Tsh.jpeg" ~ 6,
      compensation_image.A == "7Tsh.jpeg" ~ 7,
      compensation_image.A == "8Tsh.jpeg" ~ 8,
      compensation_image.A == "9Tsh.jpeg" ~ 9,
      compensation_image.A == "10Tsh.jpeg" ~ 10
    ),
    compB = case_when(
      compensation_image.B == "0Tsh.jpeg" ~ 0,
      compensation_image.B == "1Tsh.jpeg" ~ 1,
      compensation_image.B == "2Tsh.jpeg" ~ 2,
      compensation_image.B == "3Tsh.jpeg" ~ 3,
      compensation_image.B == "4Tsh.jpeg" ~ 4,
      compensation_image.B == "5Tsh.jpeg" ~ 5,
      compensation_image.B == "6Tsh.jpeg" ~ 6,
      compensation_image.B == "7Tsh.jpeg" ~ 7,
      compensation_image.B == "8Tsh.jpeg" ~ 8,
      compensation_image.B == "9Tsh.jpeg" ~ 9,
      compensation_image.B == "10Tsh.jpeg" ~ 10
    )
  )


# Step 1: Filter out tie situations
filtered_data <- dce_compensation_dataset %>%
  filter(compA != compB)

# Step 2: Calculate wins
comp_wins <- filtered_data %>%
  mutate(
    winner_comp = case_when(
      option_selected == 1 ~ compA,
      option_selected == 2 ~ compB
    )
  ) %>%
  select(winner_comp) %>%
  group_by(winner_comp) %>%
  summarise(wins = n(), .groups = "drop")

# Step 3: Count total appearances
comp_appearances <- filtered_data %>%
  select(compA, compB) %>%
  pivot_longer(cols = everything(), names_to = "type", values_to = "comp") %>%
  group_by(comp) %>%
  summarise(appearances = n(), .groups = "drop")

# Step 4: Join + calculate win rate
comp_stats <- left_join(comp_appearances, comp_wins, by = c("comp" = "winner_comp")) %>%
  mutate(
    wins = replace_na(wins, 0),
    win_rate = wins / appearances
  )

# Step 5: Compute confidence intervals
comp_stats <- comp_stats %>%
  rowwise() %>%
  mutate(
    ci = list(binom.test(wins, appearances)$conf.int),
    ci_lower = ci[[1]],
    ci_upper = ci[[2]]
  ) %>%
  ungroup() %>%
  select(-ci)

# Step 6: Plot with confidence intervals
ggplot(comp_stats, aes(x = comp, y = win_rate)) +
  geom_line(group = 1, color = "blue") +
  geom_point(size = 2, color = "darkblue") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  scale_x_continuous(
    breaks = 0:10,
    labels = function(x) paste0(x, " Tsh")
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  labs(
    title = "Win Rate by Compensation Level (95% CI, Excluding Equal Pairs)",
    x = "Compensation Amount",
    y = "Win Rate"
  ) +
  theme_minimal()

# We can also *not* exclude the equal pairs: 

# # Step 1: Gather into long format to compare A vs B in a unified way
# comp_wins <- dce_compensation_dataset %>%
#   mutate(
#     winner_comp = case_when(
#       option_selected == 1 ~ compA,
#       option_selected == 2 ~ compB
#     )
#   ) %>%
#   select(winner_comp) %>%
#   group_by(winner_comp) %>%
#   summarise(wins = n(), .groups = "drop")
# 
# # Step 2: Count total appearances of each level
# comp_appearances <- dce_compensation_dataset %>%
#   select(compA, compB) %>%
#   pivot_longer(cols = everything(), names_to = "type", values_to = "comp") %>%
#   group_by(comp) %>%
#   summarise(appearances = n(), .groups = "drop")
# 
# # Step 3: Join + calculate win rate
# comp_stats <- left_join(comp_appearances, comp_wins, by = c("comp" = "winner_comp")) %>%
#   mutate(
#     wins = replace_na(wins, 0),
#     win_rate = wins / appearances
#   )
# 
## Step 4: Compute confidence intervals
# comp_stats <- comp_stats %>%
#   rowwise() %>%
#   mutate(
#     ci = list(binom.test(wins, appearances)$conf.int),
#     ci_lower = ci[[1]],
#     ci_upper = ci[[2]]
#   ) %>%
#   ungroup() %>%
#   select(-ci)
# 
# # Step 5: Plot with confidence intervals
# ggplot(comp_stats, aes(x = comp, y = win_rate)) +
#   geom_line(group = 1, color = "blue") +
#   geom_point(size = 2, color = "darkblue") +
#   geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "gray40") +
#   geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
#   scale_x_continuous(
#     breaks = 0:10,
#     labels = function(x) paste0(x, " Tsh")
#   ) +
#   scale_y_continuous(
#     limits = c(0, 1),
#     breaks = seq(0, 1, by = 0.1)
#   ) +
#   labs(
#     title = "Win Rate by Compensation Level (95% CI, Excluding Equal Pairs)",
#     x = "Compensation Amount",
#     y = "Win Rate"
#   ) +
#   theme_minimal()

```

```{r To-do: Analyze three study experiment}

# The three-study experiment asked questions about what methods people prefer. We need to analyze whether participants exhibited a preference for any particular method after controlling for the presentation order and the study it was about. 

# Want a simple linear regression controlling for these (results preference, formats preference, and clarity preference)


# Interpretation Note: Since the ranking value is greater when the participant preferred the option less, invert interpretations
# Drawn from these results (i.e. negative coef is more preference, positive coef is less preference)


results_pref_model <- lm(results_preference_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(results_pref_model)
#bptest(results_pref_model)
#Evidence suggests presence of heteroskedasticity
coeftest(results_pref_model, vcov = vcovHC(results_pref_model, type = "HC0", cluster = ~respondentid))

formats_pref_model <- lm(formats_preference_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(formats_pref_model)
#bptest(formats_pref_model)
#Evidence suggests presence of heteroskedasticity
coeftest(formats_pref_model, vcov = vcovHC(formats_pref_model, type = "HC0", cluster = ~respondentid))

formats_clarity_model <- lm(formats_clarity_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(formats_clarity_model)
#bptest(formats_clarity_model)
#Evidence suggests against presence of heteroskedasticity, but code available below for robust standard errors
coeftest(formats_clarity_model, vcov = vcovHC(formats_clarity_model, type = "HC0"), cluster = ~respondentid)

```

```{r To-do: Analyze activity data}

# We asked questions about what activities each participant was involved with. I believe this question set was designed to provide an indication of whether or not individuals correctly recalled participating in the experiment. 

    #First-- are people recalling accurately? Yes/No

    #Anything else we can say about it?

```

```{r To-do: Summarize comment variables}

# The comment variables might provide some qualitative information, but it's in Swahili. Can we compile it here and translate it?

```

```{r To-do: Summary Statistics Table: Convert factor/numerical}

#      - Several variables are not categorized as factor variables when they should
#      - The compensation variables for A/B are not converted to numerical values in the fulldata dataset, this was instead done in the dceanalysis dataset in the [Analyze DCE data] sections. Let's get that moved over to data cleaning so it's correctly coded as numerical

```

```{r To-do: Analyze the rank results methods 1-9 (What are the top method preferences?)}

```

```{r To-do: Summarize challenges participants identified}

```



