---
title: "ER2 Kagera Data Analysis 1"
author: "Elyse St Sauver"
date: "2025-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse, stargazer, ggplot2, sandwich)
```

# Initial Data Cleaning

Notes for Mira: \\
  - The [COMPLETE] tag means the task is fully done. \\
  - Three asterisks (***) mean this is a note to bring up with Henry and/or the enumerators. \\
  - The [To-Do] tag means the task is still incomplete. \\
  
  ____________________________________________________________________________________________________________________________________________________

  Let's import the data and check for abnormalities. More specifically, we're importing the data and looking for odd patterns like: \\ 
  - NA values where there should be something else (like a 0 or a "False") \\
  - Columns where every/nearly every participant responded the same \\
  - Variables out of order \\
  - Columns that need reformatting (ex. "1 - Least satisfied" and "2" in the same column, or "1 2 3 0 9" which should be one column each for "1" "2", etc.) \\
  - Anything else that looks unusual or wrong \\
  
  Some NA values are fine, we're just especially concerned with those in columns where we need to do analysis. Those include the DCE responses*, 3-study method questions (Haushofer, etc), the activity response section, and the demographics. To start, take a look at the data and see if anything looks weird to you, I've typed up my initial thoughts below. When I figured something out while working with the data, I indicate it below as well. \\
  
  *You might notice the returningresults_merged dataset doesn't have the DCE data. For some reason, it's separate in SurveyCTO-- that's okay, we just have to join the datasets together. To begin with, look at the datasets separately and we'll join them in a later step. \\
  

```{r Non-DCE Data Import}
kageradata <- read.csv("returningresults_merged.csv")
```

Data Notes: 
  - ID indicator is respondentID or respondent_index
  - For joining with DCE data, join column is SET.OF.dce_game

Data Issues:
  - [COMPLETE][No code needed] what is respo_confirm? 
          Answer --> Some respondents did not confirm and are replaced 
  - *** part_study_1, who_participated --> not complete
  - *** contact_research --> not complete ("Did you get contact information for researchers"? Confirm what this question is)
  - *** clear_plans, ask_results --> almost empty
  
  - [To-Do] keep_documentation/have_documentation might be in the wrong order (Confirm order)
  - [To-Do] num_past_studies has NAs that Should be 0 (when past_study_participation is 0) 
  
  - *** many 0s for past_study_participation, so much of the activity response section is empty
  - *** future_study_willingness --> not complete
  
  
```{r DCE Data Import}
dcedata <- read.csv("dce_returningresults_merged.csv")
#scenarios <- read.csv("scenario_dataset_pilot.csv")
```

DCE Data Notes:
    - No ID indicator, for joining with Kagera data, join column is SET.OF.dce_game
    - DCE data has 10 observations per ID, so it will be a many-to-one join (and that's okay)
    
DCE Issues: 
    - [COMPLETE][Join Sets] Need to parse the game_matrix (stitched_output_##.jpg) to the actual levels and features from the Excel sheet. This means another join
    - [COMPLETE][Join Sets] Join on the game_matrix column (to the "image" column in the Excel spreadsheet of DCE features and levels)

# To-Do for Both Datasets: \\

  Each section below is organized to address one of these points. Oustanding tasks (to-dos) are tagged with that in the section heading

  - [To-Do] Resolve items in Issues sections
  - [COMPLETE][Data cleaning] Distribute rank_results_methods to their own columns
  - [COMPLETE][Data cleaning] Current rank_results_methods_1, rank_results_methods_2 are useless, replace with rank *of* results method 1, etc
  - [COMPLETE][Data cleaning] Distribute first_position, second_position, third_position to "first_study", "first_method", "second study", etc.
  - [COMPLETE][Data cleaning] Distribute rank_results_preference to Study 1 Rank column, Study 2 Rank column, etc. 
      - [COMPLETE][Data cleaning] Do the same for rank_formats_preference and rank_formats_clarity
  - [To-Do] Analyze three study experiment (especially the "likelihood" variables)
  - [COMPLETE][Join Sets] Join DCE data with levels/features sheet
  - [COMPLETE][Join Sets] Join DCE data post-merge with levels/featuers to the kagera data, and clean
  - [To-Do] Analyze DCE data
      - [To-Do] Regress likelihood of choosing A when each feature level is present in A, present in B. 
      - [To-Do] Create graph of likelihood of choosing A/B given compensation level of A/B. 
      - Pairwise comparison?
  - [To-Do] Can we do anything with the activity data? It's very incomplete, but let's try...
  - [To-Do] Check out comment variables (exercise_comment and exercise_comment_oth for DCE comments, end_commet for overall comments)
  - [To-Do] Create a table of summary statistics for each variable 
      - Number of responses (and response rate %)
      - If numerical: Median, mean, range, standard deviation of responses for numerical
      - If categorical: Tabulation (Count of each response type)

```{r Join Sets}
# Augment the DCE dataset with the scenarios set
  # Check for respondent index and image label presence, then join on those variables
  scenarios <- select(scenarios, -c(respondent_ID, choicenumber, choicenumber2, 
                                    participants_title.A, participants_title.B, 
                                    community_title.A, community_title.B, 
                                    policymakers_title.A, policymakers_title.B, 
                                    compensation_title.A, compensation_title.B, 
                                    researchfunding_title.A, researchfunding_title.B))
  
  dcedata |> 
    filter(is.na(respondent_index) | is.na(game_matrix))
  
  kageradata |> 
    filter(is.na(respondent_index))
  
  scenarios |>
    filter(is.na(image))

  # Augment the DCE dataset with the scenarios dataset (so that we have a column with each feature's level for A and B)
  dcedata_aug <- left_join(dcedata, scenarios, by = join_by(game_matrix == image), suffix = c(".Collected", ".Generated"))

  # Join the augmented DCE dataset to the Kagera data
  fulldata <- left_join(kageradata, dcedata_aug, by = c("SET.OF.dce_game"))
```

```{r Data Cleaning}
# Cleaning the main Kagera dataset first. 

  # Some respondants did not confirm, so they have been replaced with other respondants. Dropping the nonresponding rows. 
fulldata <- subset(fulldata, respo_confirm == 1)

# Rank varaiables --> columns for radio, sms, etc. and cell values are the rank designated by participant
  # Some of the columns have collections of data that should be distributed into individual columns. These are resolved here. 
  # rank_results_methods
  # first_position, second_position, third_position
  # rank_results_preference
  # rank_formats_preference
  # rank_formats_clarity
max_splits <- max(sapply(strsplit(fulldata$rank_results_methods, " "), length)) # Determine max splits
fulldata <- fulldata %>%
  tidyr::separate(rank_results_methods, into = paste0("rank_results_methods_", 1:max_splits), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_results_preference, into = paste0("rank_results_preference_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_formats_preference, into = paste0("rank_formats_preference_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(rank_formats_clarity, into = paste0("rank_formats_clarity_", 1:3), sep = " ", convert = TRUE, fill = "right") %>%
  #Now separate out study title and method
  tidyr::separate(first_position, into = c("first_study", "first_method"), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(second_position, into = c("second_study", "second_method"), sep = " ", convert = TRUE, fill = "right") %>%
  tidyr::separate(third_position, into = c("third_study", "third_method"), sep = " ", convert = TRUE, fill = "right")


kanalysis <- fulldata %>%
  mutate(across(77:85, ~ case_when(
    . == "not satisfied" ~ as.character(1),
    . == "very satisfied" ~ as.character(5),
    TRUE ~ as.character(.)
  )),
  across(45, ~ case_when(
    . == "Not busy at all" ~ as.character(1),
    . == "Very busy" ~ as.character(5),
    TRUE ~ as.character(.)
  )),
  across(88, ~ case_when(
    . == "Least interested" ~ as.character(1),
    . == "Most interested" ~ as.character(5),
    TRUE ~ as.character(.)
  )))

# Generate dummy var for study, position, method

threestudy_analysis <- select(kanalysis, c(18, 222:236))

threestudy_analysis <- threestudy_analysis %>%
  pivot_longer(cols = c("first_study", "first_method", "second_study", "second_method", "third_study", "third_method"),
               names_to = c("order", ".value"),
               names_sep = "_") %>%
  mutate(order = factor(order, levels = c("first", "second", "third")))

threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_results_preference_1", "rank_results_preference_2", "rank_results_preference_3"))
threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_formats_preference_1", "rank_formats_preference_2", "rank_formats_preference_3"))
threestudy_analysis <- dummy_cols(threestudy_analysis, select_columns = c("rank_formats_clarity_1", "rank_formats_clarity_2", "rank_formats_clarity_3"))
threestudy_analysis$results_preference_ranking <- NA
threestudy_analysis$formats_preference_ranking <- NA
threestudy_analysis$formats_clarity_ranking <- NA
#Repeat for formats preference, formats clarity
j = 1

while(j <= nrow(threestudy_analysis)) {
    current_row <- threestudy_analysis[j,]
    order_num = case_when(
      current_row$order == "first" ~ 1,
      current_row$order == "second" ~ 2,
      current_row$order == "third" ~ 3
    )
    results_preference_ranking = case_when(
      order_num == 1 & current_row$rank_results_preference_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_results_preference_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_results_preference_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_results_preference_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_results_preference_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_results_preference_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_results_preference_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_results_preference_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_results_preference_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "results_preference_ranking"] <- results_preference_ranking
    formats_preference_ranking = case_when(
      #order_num == 1 & current_row$rank_formats_preference_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_formats_preference_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_formats_preference_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_formats_preference_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_formats_preference_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_formats_preference_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_formats_preference_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_formats_preference_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_formats_preference_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "formats_preference_ranking"] <- formats_preference_ranking
    formats_clarity_ranking = case_when(
      order_num == 1 & current_row$rank_formats_clarity_1_1 == 1 ~ 1,
      order_num == 2 & current_row$rank_formats_clarity_1_2 == 1 ~ 1,
      order_num == 3 & current_row$rank_formats_clarity_1_3 == 1 ~ 1,
      order_num == 1 & current_row$rank_formats_clarity_2_1 == 1 ~ 2,
      order_num == 2 & current_row$rank_formats_clarity_2_2 == 1 ~ 2,
      order_num == 3 & current_row$rank_formats_clarity_2_3 == 1 ~ 2,
      order_num == 1 & current_row$rank_formats_clarity_3_1 == 1 ~ 3,
      order_num == 2 & current_row$rank_formats_clarity_3_2 == 1 ~ 3,
      order_num == 3 & current_row$rank_formats_clarity_3_3 == 1 ~ 3,
    )
    threestudy_analysis[j, "formats_clarity_ranking"] <- formats_clarity_ranking
    j <- j + 1
}

threestudy_long <- select(threestudy_analysis, c("respondentid", "order", "study", "method", "results_preference_ranking", "formats_preference_ranking", "formats_clarity_ranking"))
```

```{r To-do: Resolve items in the datasets' Issues sections}

# Two left. These fixes probably belong in the data cleaning section once they're implemented.
#   - keep_documentation/have_documentation might be in the wrong order (Confirm order in dataset matches with the survey spreadsheet)
#   - num_past_studies has NAs that I think should be 0 when past_study_participation is 0


```

```{r To-do: Analyze three study experiment (especially the "likelihood" variables)}

# The three-study experiment asked questions about what methods people prefer. We need to analyze whether participants exhibited a preference for any particular method after controlling for the presentation order and the study it was about. 

# Want a simple linear regression controlling for these (results preference, formats preference, and clarity preference)


# Interpretation Note: Since the ranking value is greater when the participant preferred the option less, invert interpretations
# Drawn from these results (i.e. negative coef is more preference, positive coef is less preference)


results_pref_model <- lm(results_preference_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(results_pref_model)
#bptest(results_pref_model)
#Evidence suggests presence of heteroskedasticity
coeftest(results_pref_model, vcov = vcovHC(results_pref_model, type = "HC0", cluster = ~respondentid))

formats_pref_model <- lm(formats_preference_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(formats_pref_model)
#bptest(formats_pref_model)
#Evidence suggests presence of heteroskedasticity
coeftest(formats_pref_model, vcov = vcovHC(formats_pref_model, type = "HC0", cluster = ~respondentid))

formats_clarity_model <- lm(formats_clarity_ranking ~ method + study + order + respondentid, data = threestudy_long)
#summary(formats_clarity_model)
#bptest(formats_clarity_model)
#Evidence suggests against presence of heteroskedasticity, but code available below for robust standard errors
coeftest(formats_clarity_model, vcov = vcovHC(formats_clarity_model, type = "HC0"), cluster = ~respondentid)

```

```{r To-do: Analyze DCE data}

#- Regress likelihood of choosing A when each feature level is present in A, present in B. 

# Add columns for each of 5 features, levels, for each A and B (1 if present, 0 else)
features <- colnames(dcedata_aug)[10:20]
features <- features[features != "compset"]
dceanalysis <- dummy_cols(dcedata_aug, select_columns = features)

# If feature is the same in A and B, make 0. For continuous variables, use delta

# Force shared feature levels across A and B equal to 0
dceanalysis <- dceanalysis %>%
  rowwise() %>%
  mutate(across(starts_with("participants_image.A_") | starts_with("participants_image.B_"), 
                ~ if_else(participants_image.A == participants_image.B, as(0, class(.)), .)),
         across(starts_with("community_image.A_") | starts_with("community_image.B_"), 
                ~ if_else(community_image.A == community_image.B, as(0, class(.)), .)),
         across(starts_with("policymakers_image.A_") | starts_with("policymakers_image.B_"), 
                ~ if_else(policymakers_image.A == policymakers_image.B, as(0, class(.)), .)),
         across(starts_with("compensation_image.A_") | starts_with("compensation_image.B_"), 
                ~ if_else(compensation_image.A == compensation_image.B, as(0, class(.)), .)),
         across(starts_with("researchfunding_image.A_") | starts_with("researchfunding_image.B_"), 
                ~ if_else(researchfunding_image.A == researchfunding_image.B, as(0, class(.)), .))) %>%
  ungroup()

dceanalysis <- dceanalysis %>%
  rename(option_selected = dce_potion)

dceanalysis <- dceanalysis %>%
  mutate (
    option_selected = case_when(
      option_selected == "Scenation 1" ~ 1,
      option_selected == "Scenation 2" ~ 0
    )
  )

# Create comp_delta and funding_delta for continuous features
dceanalysis$comp_delta <- NA
dceanalysis$funding_delta <- NA
i = 1

while(i <= nrow(dceanalysis)) {
    current_row <- dceanalysis[i,]
    compA <- 0
    compB <- 0
    fundingA <- 0
    fundingB <- 0
    compA = case_when(
      current_row$compensation_image.A_0Tsh.jpeg == 1 ~ 0,
      current_row$compensation_image.A_1Tsh.jpeg == 1 ~ 1,
      current_row$compensation_image.A_2Tsh.jpeg == 1 ~ 2,
      current_row$compensation_image.A_3Tsh.jpeg == 1 ~ 3,
      current_row$compensation_image.A_4Tsh.jpeg == 1 ~ 4,
      current_row$compensation_image.A_5Tsh.jpeg == 1 ~ 5,
      current_row$compensation_image.A_6Tsh.jpeg == 1 ~ 6,
      current_row$compensation_image.A_7Tsh.jpeg == 1 ~ 7,
      current_row$compensation_image.A_8Tsh.jpeg == 1 ~ 8,
      current_row$compensation_image.A_9Tsh.jpeg == 1 ~ 9,
      current_row$compensation_image.A_10Tsh.jpeg == 1 ~ 10
    )
    compB = case_when(
      current_row$compensation_image.B_0Tsh.jpeg == 1 ~ 0,
      current_row$compensation_image.B_1Tsh.jpeg == 1 ~ 1,
      current_row$compensation_image.B_2Tsh.jpeg == 1 ~ 2,
      current_row$compensation_image.B_3Tsh.jpeg == 1 ~ 3,
      current_row$compensation_image.B_4Tsh.jpeg == 1 ~ 4,
      current_row$compensation_image.B_5Tsh.jpeg == 1 ~ 5,
      current_row$compensation_image.B_6Tsh.jpeg == 1 ~ 6,
      current_row$compensation_image.B_7Tsh.jpeg == 1 ~ 7,
      current_row$compensation_image.B_8Tsh.jpeg == 1 ~ 8,
      current_row$compensation_image.B_9Tsh.jpeg == 1 ~ 9,
      current_row$compensation_image.B_10Tsh.jpeg == 1 ~ 10
    )
    fundingA = case_when(
      current_row$researchfunding_image.A_research0.jpeg == 1 ~ 0,
      current_row$researchfunding_image.A_research2.jpeg == 1 ~ 2,
      current_row$researchfunding_image.A_research4.jpeg == 1 ~ 4,
      current_row$researchfunding_image.A_research6.jpeg == 1 ~ 6,
      current_row$researchfunding_image.A_research8.jpeg == 1 ~ 8,
      current_row$researchfunding_image.A_research10.jpeg == 1 ~ 10,
      current_row$researchfunding_image.A_research12.jpeg == 1 ~ 12,
      current_row$researchfunding_image.A_research14.jpeg == 1 ~ 14,
      current_row$researchfunding_image.A_research16.jpeg == 1 ~ 16,
      current_row$researchfunding_image.A_research18.jpeg == 1 ~ 18,
      current_row$researchfunding_image.A_research20.jpeg == 1 ~ 20,
      .default = 0
    )
    fundingB = case_when(
      current_row$researchfunding_image.B_research0.jpeg == 1 ~ 0,
      current_row$researchfunding_image.B_research2.jpeg == 1 ~ 2,
      current_row$researchfunding_image.B_research4.jpeg == 1 ~ 4,
      current_row$researchfunding_image.B_research6.jpeg == 1 ~ 6,
      current_row$researchfunding_image.B_research8.jpeg == 1 ~ 8,
      current_row$researchfunding_image.B_research10.jpeg == 1 ~ 10,
      current_row$researchfunding_image.B_research12.jpeg == 1 ~ 12,
      current_row$researchfunding_image.B_research14.jpeg == 1 ~ 14,
      current_row$researchfunding_image.B_research16.jpeg == 1 ~ 16,
      current_row$researchfunding_image.B_research18.jpeg == 1 ~ 18,
      current_row$researchfunding_image.B_research20.jpeg == 1 ~ 20,
      .default = 0
    )
    # Check if any comp or research funding dummy variables are == 1
    # For nonzero variables, case_when assign numerical value
    # Assign comp_delta, comp_funding equal to the differences (A - B, not absolute value since positive/negative indicates whether A or B is greater)
    dceanalysis[i, "comp_delta"] <- compA - compB
    dceanalysis[i, "funding_delta"] <- fundingA - fundingB
    i <- i + 1
}


## DCE Linear Regression Analysis

# This regression analysis regressed the option selected (A = 1, B = 0) on the presence of the various features and levels therein. Results are presented with robust standard errors and clustered at the respondent level unless otherwise specified.


dce_model <- lm(data = dceanalysis, 
                option_selected ~ 
                  #Feature Levels
                participants_image.A_participant1.jpeg
                + participants_image.A_participant2.jpeg
                + participants_image.A_participant3.jpeg
                + community_image.A_community1.jpeg
                + community_image.A_community2.jpeg
                + community_image.A_community3.jpeg
                + policymakers_image.A_policy1.jpeg
                + policymakers_image.A_policy2.jpeg
                + policymakers_image.A_policy3.jpeg
                + participants_image.B_participant1.jpeg
                + participants_image.B_participant2.jpeg
                + participants_image.B_participant3.jpeg
                + community_image.B_community1.jpeg
                + community_image.B_community2.jpeg
                + community_image.B_community3.jpeg
                + policymakers_image.B_policy1.jpeg
                + policymakers_image.B_policy2.jpeg
                + policymakers_image.B_policy3.jpeg
                + comp_delta
                + funding_delta
                  #Individual Controls
                + respondent_index
                + game_index
)

#summary(dce_model)

#Test for heteroskedasticity
bptest(dce_model)
#Evidence suggests against presence of heteroskedasticity, but code available below for robust standard errors

coeftest(dce_model, vcov = vcovHC(dce_model, type = "HC0"), cluster = ~ respondentid)

#corrplot(cor(dceanalysis[c(2,3,6, 21:29, 52:60, 83, 84)]), type = "upper", diag = FALSE, tl.cex = 0.5)

```

```{r To-do: DCE Graph of chioce given comp level}

      #- Create graph of likelihood of choosing A/B given compensation level of A/B. 

```

```{r To-do: Analyze activity data...? Very incomplete, but let's see if we can do any analysis}

# We asked questions about what activities each participant was involved with. I believe this question set was designed to provide an indication of whether or not individuals correctly recalled participating in the experiment. 

    #First-- are people recalling accurately? Yes/No

    #Anything else we can say about it?

```

```{r To-do: Check out comment variables (exercise_comment and exercise_comment_oth for DCE comments, end_commet for overall comments)}

# The comment variables might provide some qualitative information, but it's in Swahili. Can we compile it here and translate it?

```

```{r To-do: Create a table of summary statistics for each variable}

# We basically want summary statistics for every var and a table with everything labeled clearly. Ideally have the question on the left, stats on the right.
#   - If numerical: Median, mean, range, standard deviation of responses for numerical
#   - If categorical: Tabulation (Count of each response type)
#   - For everything, we want a number of responses (N) and response rate (%)

```


