---
title: "ER2 Data Codebook"
author: "Elyse St Sauver"
date: "2025-04-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
```

# ER2 Codebook

#To - Do:
- Indicate factor/numerical/ordinal (meaning first, second, etc)/date
    - Numerical indicates continuous numerical variables where the quantity has an independent meaning (e.g. age, years of schooling, etc)
    - Ordinal indicates discrete numerical variables that only have meaning relative to the other values observed (e.g. 1st/2nd/etc)
    - By default, code binary variables as factors unless otherwise noted
- Create interactive table (alphabetical sort, sort by type, etc.)

```{r Raw text of corresponding variable names and types}
raw_text <- "
location # factor,
game_index # ordinal,
choicenumber # ordinal,
game_matrix # factor,
dce_potion # factor,
PARENT_KEY #factor,
KEY.x # factor,
SET.OF.dce_game # factor,
participants_image.A # factor,
community_image.A # factor,
policymakers_image.A # factor,
compensation_image.A # factor,
researchfunding_image.A # factor,
compset # factor,
participants_image.B # factor,
community_image.B # factor,
policymakers_image.B # factor,
compensation_image.B # factor,
researchfunding_image.B # factor,
SubmissionDate # datetime,
starttime # datetime,
endtime # datetime,
deviceid # factor,
devicephonenum  # factor,
username  # factor,
device_info # factor,
duration # numerical,
caseid # factor,
text_audit # unknown,
comments # factor,
start_time # datetime,
interviewer # factor,
int_name # factor,
districtID # factor,
district_name # factor,
wardID # factor,
ward_name # factor,
villageID # factor,
village_name # factor,
respondentID # factor,
control # unknown,
gps.Latitude # numerical,
gps.Longitude # numerical ,
gps.Altitude # numerical,
gps.Accuracy # numerical,
respondent_name # factor,
respondent_index # factor,
respo_confirm  # factor,
part_study_1 # factor,
who_participated_1 # factor,
speak_othermember_1 # factor,
replacement_respondent # factor,
part_study_2 # factor,
who_participated_2 # factor,
speak_othermember_2 # factor,
replacement_name # factor,
consent # factor,
start_sec1 # datetime,
resp_age # numerical,
resp_gender # factor,
resp_marital # factor,
hh_adults # numerical,
hh_children # numerical,
hh_teen # numerical,
resp_education # numerical,
work_seven_days # numerical,
work_three_month # numerical,
resp_busy # ordinal,
start_sec2 # datetime,
remember_study # factor,
hear_study # factor,
hear_study_oth # factor,
enrol_study # factor,
enrol_study_oth # factor,
receive_result # factor,
explain_study # factor,
understand_study # factor,
study_documentation # factor,
keep_documentation # factor,
have_documentation # factor,
researchers_names # factor,
contact_research # factor,
informed_consent # factor,
informed_study_results # factor,
clear_plans # factor,
ask_results # factor,
interviewer_interaction # factor,
activity_1 # factor,
activity_1b # factor,
activity_2 # factor,
activity_2b # factor,
activity_3 # factor,
activity_3b # factor,
activity_4 # factor,
activity_4b # factor,
activity_5 # factor,
activity_5b # factor,
activity_6 # factor,
activity_6b # factor,
satisfied_compensation # ordinal,
satisfied_time # ordinal,
satisfied_interaction # ordinal,
satisfied_information # ordinal,
info_received_during_study # ordinal,
info_received_end_study # ordinal,
clarity_timelines # ordinal,
relevance_personal # ordinal,
relevance_community # ordinal,
lasting_impacts # factor,
lasting_impacts_description # factor,
future_participation_interest # ordinal,
challenges_encountered # factor,
challenges_description_oth2 # factor,
challenges_resolution # factor,
start_sec3 # datetime,
start_sec4 # datetime,
past_study_participation # factor,
num_past_studies # numerical,
study_activities # factor,
study_activities_1 # factor,
study_activities_2 # factor,
study_activities_3 # factor,
study_activities_4 # factor,
study_activities_5 # factor,
study_activities_6 # factor,
study_activities_7 # factor,
study_activities_8 # factor,
study_activities_9 # factor,
study_activities_10 # factor,
study_activities_11 # factor,
study_activities_12 # factor,
study_activities_13 # factor,
study_activities_oth # factor,
studies_returned_info # numerical,
audio_results_received # factor,
audio_message_listened # factor,
audio_results_understandable # ordinal,
sms_results_received # factor,
sms_message_read # factor,
sms_results_understandable # ordinal,
website_results_received # factor,
website_link_clicked # factor,
website_results_understandable # ordinal,
flyer_results_received # factor,
flyer_read # factor,
flyer_results_understandable # ordinal,
posted_flyer_results_received # factor,
posted_flyer_read # factor,
posted_flyer_results_understandable # ordinal,
social_media_results_seen # factor,
social_media_interacted # factor,
social_media_results_understandable # ordinal,
video_results_received # factor,
video_watched # factor,
video_results_understandable # ordinal,
public_meeting_invited # factor,
public_meeting_attended # factor,
public_meeting_results_understandable # ordinal,
private_meeting_invited # factor,
private_meeting_attended # factor,
private_meeting_results_understandable # ordinal,
phone_call_results_heard # factor,
phone_call_answered # factor,
phone_call_results_understandable # ordinal,
other_results_received # factor,
other_results_received_oth # factor,
other_results_understandable # ordinal,
results_wait_time_perception # ordinal,
results_return_time_satisfaction # factor,
future_study_willingness # factor,
past_study_challenges_details # factor,
past_study_challenges_addressed_by # factor,
past_study_challenges_addressed_by_1 # factor,
past_study_challenges_addressed_by_2 # factor,
past_study_challenges_addressed_by_3 # factor,
past_study_challenges_addressed_by_4 # factor,
past_study_challenges_addressed_by_5 # factor,
past_study_challenges_addressed_by_6 # factor,
past_study_challenges_addressed_by_7 # factor,
past_study_challenges_addressed_by_8 # factor,
past_study_challenges_addressed_by_9 # factor,
past_study_challenges_addressed_by_10 # factor,
past_study_challenges_addressed_by_oth # factor,
other_participant_challenges_heard # factor,
other_participant_challenges_heard_1 # factor,
other_participant_challenges_heard_2 # factor,
other_participant_challenges_heard_3 # factor,
other_participant_challenges_heard_4 # factor,
other_participant_challenges_heard_5 # factor,
other_participant_challenges_heard_6 # factor,
other_participant_challenges_heard_7 # factor,
other_participant_challenges_heard_8 # factor,
other_participant_challenges_heard_9 # factor,
other_participant_challenges_heard_10 # factor,
other_participant_challenges_heard_oth # factor,
other_participant_challenges_details # factor,
other_participant_challenges_addressed_by # factor,
other_participant_challenges_addressed_by_1 # factor,
other_participant_challenges_addressed_by_2 # factor,
other_participant_challenges_addressed_by_3 # factor,
other_participant_challenges_addressed_by_4 # factor,
other_participant_challenges_addressed_by_5 # factor,
other_participant_challenges_addressed_by_6 # factor,
other_participant_challenges_addressed_by_7 # factor,
other_participant_challenges_addressed_by_8 # factor,
other_participant_challenges_addressed_by_9 # factor,
other_participant_challenges_addressed_by_10 # factor,
who_involved # factor,
who_involved_1 # factor,
who_involved_2 # factor,
who_involved_3 # factor,
who_involved_4 # factor,
who_involved_5 # factor,
who_involved_6 # factor,
who_involved_7 # factor,
who_involved_8 # factor,
who_involved_9 # factor,
who_involved_10 # factor,
start_sec6 # datetime,
important_to_return_results_resources # ordinal,
returning_results_shows_respect # ordinal,
participants_right_to_results # ordinal,
importance_of_results_returned # factor,
preferred_results_return_method # factor,
study_participants # factor,
non_participants_research_communities # factor,
local_community_leaders # factor,
local_government_officials # factor,
foreign_government_officials # factor,
religious_leaders # factor,
other_researchers # factor,
result_timeline # factor,
rank_results_methods_1 # ordinal,
rank_results_methods_2 # ordinal,
rank_results_methods_3 # ordinal,
rank_results_methods_4 # ordinal,
rank_results_methods_5 # ordinal,
rank_results_methods_6 # ordinal,
rank_results_methods_7 # ordinal,
rank_results_methods_8 # ordinal,
rank_results_methods_9 # ordinal,
start_sec7 # datetime,
random # unknown,
random_choice # unknown,
first_study # factor,
first_method # factor,
second_study # factor,
second_method # factor,
third_study # factor,
third_method # factor,
rank_results_preference_1 # ordinal,
rank_results_preference_2 # ordinal,
rank_results_preference_3 # ordinal,
rank_formats_preference_1 # ordinal,
rank_formats_preference_2 # ordinal,
rank_formats_preference_3 # ordinal,
rank_formats_clarity_1 # ordinal,
rank_formats_clarity_2 # ordinal,
rank_formats_clarity_3 # ordinal,
likelihood_watch_video_results # ordinal,
likelihood_read_sms_results # ordinal,
likelihood_listen_audio_results # ordinal,
read_sms # factor,
start_sec8 # datetime,
game_size # unknown,
dce_game_count # numerical,
understood_exercise # factor,
exercise_comment # factor,
exercise_comment_oth # factor,
start_sec9 # datetime,
own_mobile_phone # factor,
own_smartphone # factor,
received_messages_30days # factor,
interested_receive_result # factor,
resp_number # factor,
resp_number_own # factor,
connected_smartphone # factor,
interview_result # factor,
end_commet # factor,
end_time # datetime,
instanceID # factor,
instanceName # factor,
formdef_version # factor,
KEY.y # factor
"
```

```{r Create interactive table of variables and types}
# Clean and prepare the data
lines <- unlist(strsplit(raw_text, "\n"))
lines <- gsub(",\\s*$", "", lines)
lines <- lines[lines != ""]

split_lines <- strsplit(lines, "#")
cleaned_data <- lapply(split_lines, function(x) trimws(x))
codebook <- do.call(rbind, cleaned_data)
colnames(codebook) <- c("Variable Name", "Type")
codebook <- as.data.frame(codebook, stringsAsFactors = FALSE)

# Show the interactive data table
datatable(codebook, 
          options = list(pageLength = 25, autoWidth = TRUE),
          rownames = FALSE,
          filter = 'top',
          caption = 'Interactive Data Dictionary')

write.csv(codebook, "codebook.csv", row.names = FALSE)

```

