---
title: "ER2 Kagera Data Analysis 1"
author: "Elyse St Sauver"
date: "2025-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse, stargazer, gpplot2)
```

# Initial Data Cleaning

Notes for Mira: \\
  Let's import the data and check for abnormalities. More specifically, we're importing the data and looking for odd patterns like: \\ 
  - NA values where there should be something else (like a 0 or a "False") \\
  - Columns where every/nearly every participant responded the same \\
  - Variables out of order \\
  - Columns that need reformatting (ex. "1 - Least satisfied" and "2" in the same column, or "1 2 3 0 9" which should be one column each for "1" "2", etc.) \\
  - Anything else that looks unusual or wrong \\
  
  Some NA values are fine, we're just especially concerned with those in columns where we need to do analysis. Those include the DCE responses*, 3-study method questions (Haushofer, etc), the activity response section, and the demographics. To start, take a look at the data and see if anything looks weird to you, I've typed up my initial thoughts below. When I figured something out while working with the data, I indicate it below as well. \\
  
  *You might notice the returningresults_merged dataset doesn't have the DCE data. For some reason, it's separate in SurveyCTO-- that's okay, we just have to join the datasets together. To begin with, look at the datasets separately and we'll join them in a later step. \\
  

```{r Non-DCE Data Import}

kageradata <- read.csv("returningresults_merged.csv")

```

Data Notes: 
  - ID indicator is respondentID or respondent_index
  - For joining with DCE data, join column is SET.OF.dce_game

Data Issues:
  - what is respo_confirm? 
          Answer --> Some respondents did not confirm and are replaced 
  - * part_study_1, who_participated --> not complete
  - * contact_research --> not complete ("Did you get contact information for researchers"? Confirm what this question is)
  - keep_documentation/have_documentation might be in the wrong order (Confirm order)`
  - * clear_plans, ask_results --> almost empty
  - num_past_studies has NAs that Should be 0 (when past_study_participation is 0) 
  - * many 0s for past_study_participation, so much of the activity response section is empty
  - * future_study_willingness --> not complete
  
  
```{r DCE Data Import}

dcedata <- read.csv("dce_returningresults_merged.csv")

```

DCE Data Notes:
    - No ID indicator, for joining with Kagera data, join column is SET.OF.dce_game
    - DCE data has 10 observations per ID, so it will be a many-to-one join (and that's okay)
    
DCE Issues: 
    - Need to parse the game_matrix (stitched_output_##.jpg) to the actual levels and features from the Excel sheet. This means another join
    - Join on the game_matrix column (to the "image" column in the Excel spreadsheet of DCE features and levels)

# To-Do for Both Datasets: \\

  - Resolve items in Issues sections
  - Distribute rank_results_methods to their own columns
  - Current rank_results_methods_1, rank_results_methods_2 are useless, replace with rank *of* results method 1, etc
  - Distribute first_position, second_position, third_position to "first_study", "first_method", "second study", etc.
  - Distribute rank_results_preference to Study 1 Rank column, Study 2 Rank column, etc. 
      - Do the same for rank_formats_preference and rank_formats_clarity
  - Analyze three study experiment (especially the "likelihood" variables)
  - Join DCE data with levels/features sheet
  - Join DCE data post-merge with levels/featuers to the kagera data, and clean
  - Analyze DCE data
      - Regress likelihood of choosing A when each feature level is present in A, present in B. 
      - Create graph of likelihood of choosing A/B given compensation level of A/B. 
      - Pairwise comparison?
  - Can we do anything with the activity data? It's very incomplete, but let's try...
  - Check out comment variables (exercise_comment and exercise_comment_oth for DCE comments, end_commet for overall comments)
  - Create a table of summary statistics for each variable 
      - Number of responses (and response rate %)
      - If numerical: Median, mean, range, standard deviation of responses for numerical
      - If categorical: Tabulation (Count of each response type)
      

```{r Data Cleaning}

# Cleaning the main Kagera dataset first. 

  # Some respondants did not confirm, so they have been replaced with other respondants. Dropping the nonresponding rows. 
kageradata <- subset(kageradata, respo_confirm == 1)

  # The column num_past_studies should be 0 when past_study_participation is 0. Fixing that here
    #   [ CONFIRM, DOES PAST_STUDY_PARTICIPATION INCLUDE KAGERA? IF YES THEN SHOULD BE 1, NOT NA OR 0]

  # Some of the columns have collections of data that should be distributed into individual columns. These are resolved here. 
  # rank_results_methods
  # first_position, second_position, third_position
  # rank_results_preference
  # rank_formats_preference
  # rank_formats_clarity


  # Here is where we should join the collected DCE data with our spreadsheet of each game's corresponding A/B levels for each feature. 

  # Join the augmented DCE dataset to the Kagera data
fulldata <- left_join(kageradata, dcedata, by = c("SET.OF.dce_game"))

```

