---
title: "DCE Work 2-18-2025"
author: "Elyse St Sauver"
date: "2025-02-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(jpeg)

set.seed(2025)
```

# Initalizing Code and Generating the Scenario Pair Dataset

This code sets up the attributes we'll use in each scenario, along with the levels available for each set. Right now, I'm using numbers for the attribute levels for compactness, but this is easily changeable later. 

```{r Set attributes, levels, and number of pairs}
attributes = c("participants",
               "community",
               "policymakers",
               "compensation",
               "researchfunding")

attributesubset = c("participants",
                    "community",
                    "policymakers",
                    "researchfunding")

participantlevels = c(1, 2, 3)
communitylevels = c(1, 2, 3)
policymakerslevels = c(1,2,3)
compensationlevels = c(1,2,3,4,5,6,7,8,9,10,11) #1 == No compensation, 2 == 1,000 TSh, etc
researchfundinglevels = c(1,2,3,4,5,6,7,8,9,10,11) #1 == No additional research funding, 2 == 10 villages funding, etc

compensationlevelsubset <- compensationlevels[compensationlevels != 1] #Nonzero compensation levels

#How many scenario pairs we want to generate
total_pairs = 4500

```

This code will generate the scenario pairs by randomly selecting two attributes of the five to vary, keeping the rest fixed. Once it randomly selects the two varying attributes, it will randomly select distinct levels of the varying attributes so that scenarios A and B in the pair do not have the same value. Then, it will randomly select levels of the fixed attributes so that A and B do have the same values for the fixed attributes. It will repeat this process as specified by the "total_pairs" variable in the prior code chunk, resulting in a dataset of the scenario pairs.

```{r Generate the scenario pairs}

# Initialize the data frame that will hold each scenario pair. Each pair has two sets of 5 attributes
scenariopairdf = data.frame(
    Aparticipants = c(),
    Acommunity = c(),
    Apolicymakers = c(),
    Acompensation = c(),
    Aresearchfunding = c(),
    Bparticipants = c(),
    Bcommunity = c(),
    Bpolicymakers = c(),
    Bcompensation = c(),
    Bresearchfunding = c(),
    dominated = c(), 
    compset = c()
)

# Define a function which generates a data frame of which attributes are varying.
# compdef (2 by default) is a parameter that allows for specifying whether 
# compensation is fixed (0), varying (1) or unspecified (2). 
selectVaryingAttributes <- function(compdef = 2) {
  # Create a temporary data frame variable that holds which attributes are being varied
  tmpvary = data.frame(
    participants = c(0),
    community = c(0),
    policymakers = c(0),
    compensation = c(0),
    researchfunding = c(0)
  )
  
  if (compdef == 0) { # Compensation is fixed
    # Randomly select two varying attributes from the set of attributes without compensation
    tmpvary[1, sample(attributesubset, 2)] <- 1
  }
  if (compdef == 1) { # Compensation is varying
    tmpvary[1, "compensation"] <- 1
    # Randomly select the second varying attribute
    tmpvary[1, sample(attributesubset, 1)] <- 1
  }
  if (compdef == 2) { # Compensation is not explicitly determined as varying or fixed
    # Randomly select two varying attributes from the entire set of attributes
    tmpvary[1, sample(attributes, 2)] <- 1
  }
  
  return(tmpvary)
}

createScenarioPair <- function(tmpvary, compvary = 1) {
  # Function accepts tmpvary, a data frame that describes whether each attribute
  # is fixed (0) or varying (1), and compvary, a parameter that permits 
  # fixing compensation at zero (0) or nonzero (2) values. For varying or unspecified compensation, compvary = 1 (default).
  
  #Initialize a data frame that will be used to return the selected levels for both scenarios
  tmppair <- data.frame(
    Aparticipants = c(0),
    Acommunity = c(0),
    Apolicymakers = c(0),
    Acompensation = c(0),
    Aresearchfunding = c(0),
    Bparticipants = c(0),
    Bcommunity = c(0),
    Bpolicymakers = c(0),
    Bcompensation = c(0),
    Bresearchfunding = c(0),
    dominated = c(0), 
    compset = c(0)
  )
  
  #Generate levels for the first scenario A
  tmppair$Aparticipants <- sample(participantlevels, 1)
  tmppair$Acommunity <- sample(communitylevels, 1)
  tmppair$Apolicymakers <- sample(policymakerslevels, 1)
  tmppair$Acompensation <- sample(compensationlevels, 1) # Will be overriden by compfix = 2 or 3
  tmppair$Aresearchfunding <- sample(researchfundinglevels, 1)
  
  #Compensation attribute assignment for B
  if (compvary == 1) { #If compvary == 1 (default), assign randomly generated value that matches A if fixed, else generate different value for B
    if (tmpvary$compensation == 1) {
      # Randomly select a compensation level for B that is not equal to A's
      tmpcompensationlevels <- compensationlevels[compensationlevels != tmppair$Acompensation]
      tmppair$Bcompensation <- sample(tmpcompensationlevels, 1)
      tmppair$compset <- 1
    } else {
      tmppair$Bcompensation <- tmppair$Acompensation
      tmppair$compset <- 1
    }
  }
  if (compvary == 0) { # Fixed at no compensation
    tmppair$Acompensation <- 1
    tmppair$Bcompensation <- 1
    tmppair$compset <- 0
  }
  if (compvary == 2) { # Fixed at nonzero compensation
    tmppair$Acompensation <- sample(compensationlevelsubset, 1)
    tmppair$Bcompensation <- tmppair$Acompensation
    tmppair$compset <- 2
  }
  
  #Other attribute assignment for scenario B

  #If an attribute is fixed, set scenario B's attribute level equal to A's.
  #If an attribute is varying, set scenario B's attribute level to a random level
  #not equal to A's level.
  if (tmpvary$participants == 0) {
    tmppair$Bparticipants <- tmppair$Aparticipants
  } else {
    tmpparticipantlevels <- participantlevels[participantlevels != tmppair$Aparticipants]
    tmppair$Bparticipants <- sample(tmpparticipantlevels, 1)
  }
  
  if (tmpvary$community == 0) {
    tmppair$Bcommunity <- tmppair$Acommunity
  } else {
    tmpcommunitylevels <- communitylevels[communitylevels != tmppair$Acommunity]
    tmppair$Bcommunity <- sample(tmpcommunitylevels, 1)
  }
  
  if (tmpvary$policymakers == 0) {
    tmppair$Bpolicymakers <- tmppair$Apolicymakers
  } else {
    tmppolicymakerslevels <- policymakerslevels[policymakerslevels != tmppair$Apolicymakers]
    tmppair$Bpolicymakers <- sample(tmppolicymakerslevels, 1)
  }
  
  # Compensation is special, see above.
  
  if (tmpvary$researchfunding == 0) {
    tmppair$Bresearchfunding <- tmppair$Aresearchfunding
  } else {
    tmpresearchfundinglevels <- researchfundinglevels[researchfundinglevels != tmppair$Aresearchfunding]
    tmppair$Bresearchfunding <- sample(tmpresearchfundinglevels, 1)
  }
  
  return(tmppair)
}

# Generate a set of scenario pairs
for (i in 1:total_pairs) {
  if (i <= total_pairs/2) {
    tmppair <- createScenarioPair(selectVaryingAttributes(1), 1) # generate a scenario pair where compensation is varying
  }
  if (i > total_pairs / 2 & i <= total_pairs*0.75) {
    tmppair <- createScenarioPair(selectVaryingAttributes(0), 0)# Generate a scenario pair where compensation is fixed at zero
  } 
  if (i > total_pairs*0.75) {
    tmppair <- createScenarioPair(selectVaryingAttributes(0), 2) # Generate a scenario pair where compensation is fixed at nonzero value
  }
  scenariopairdf <- rbind(scenariopairdf, tmppair)
}
```

## Eliminating dominated scenario pairs

This code aims to eliminate scenario pairs where there is an obviously better option of the two scenarios, since asking participants to express their preference for these pairs would not be informative. To do this, it checks each attribute of the scenarios, and evaluates whether A or B is obviously better. Once it has compared each scenario's version of each attribute, if one scenario always wins (excluding ties) then that scenario pair is considered dominated, and replaced with a new randomly generated scenario pair. The new one may also be dominated, so this process runs iteratively until it checks and finds no remaining dominated pairs in the dataset.

```{r Eliminate dominated scenario pairs}

checkDominatedPairs <- function(pairdf) {
  #We'll create a count of any dominated pairs we find
  count = 0
  #Check data frame of scenario pairs for dominated pairs. 
  #Dominated pairs are defined as any pair where one scenario wins or ties pairwise comparisons for every attribute.
  for (i in 1:nrow(pairdf)) {
    row <- pairdf[i,]
    comparisonresult <- list()
    #print(i)
    #print(comparisonresult)
    #If A or B has no results returned for participants, but the other has something better, return which is better
    comparisonresult <- append(comparisonresult, case_when (
      row$Aparticipants == 1  & row$Bparticipants != 1 ~ "B",
      row$Aparticipants != 1  & row$Bparticipants == 1 ~ "A",
      row$Aparticipants == row$Bparticipants ~ "Tieparticipants"
      )
    )
    
    #If A or B has no results returned to the community, but the other has something better, return which is better
    comparisonresult <- append(comparisonresult, case_when (
      row$Acommunity == 1  & row$Bcommunity != 1 ~ "B",
      row$Acommunity != 1  & row$Bcommunity == 1 ~ "A",
      row$Acommunity == row$Bcommunity ~ "Tiecommunity"
      )
    )
    
    #If A or B has no results returned for policymakers, but the other has something better, return which is better
    comparisonresult <- append(comparisonresult, case_when (
      row$Apolicymakers == 1  & row$Bpolicymakers != 1 ~ "B",
      row$Apolicymakers != 1  & row$Bpolicymakers == 1 ~ "A",
      row$Apolicymakers == row$Bpolicymakers ~ "Tiepolicy"
      )
    )

    #If A or B has better compensation, return which is better
    comparisonresult <- append(comparisonresult, case_when (
      row$Acompensation < row$Bcompensation ~ "B",
      row$Acompensation > row$Bcompensation ~ "A",
      row$Acompensation == row$Bcompensation  ~ "Tiecomp"
      )
    )
    
    #If A or B has better research funding, return which is better
    comparisonresult <- append(comparisonresult, case_when (
      row$Aresearchfunding < row$Bresearchfunding ~ "B",
      row$Aresearchfunding > row$Bresearchfunding ~ "A",
      row$Aresearchfunding == row$Bresearchfunding  ~ "Tierf"
      )
    )
    
    #print(comparisonresult)
    if (("A" %in% comparisonresult & !("B" %in% comparisonresult) & !(NA %in% comparisonresult)) | 
        (!("A" %in% comparisonresult) & "B" %in% comparisonresult) & !(NA %in% comparisonresult)) 
      {
      pairdf$dominated[i] <- 1
      count <- count + 1
    }
  }
  print("Found the following number of dominated pairs.")
  print(count)
  
  return(pairdf)
}

replaceDominatedPairs <- function(pairdf) {
  for (i in 1:nrow(pairdf)) {
    if (pairdf$dominated[i] == 1) {
      #print(pairdf[1,])
      #Generate a new scenario pair.
      if (i <= total_pairs/2) {
        replacingpair <- createScenarioPair(selectVaryingAttributes(1), 1) # Generate a scenario pair where compensation is varying
      }
      if (i > total_pairs / 2 & i <= total_pairs*0.75) {
        replacingpair <- createScenarioPair(selectVaryingAttributes(0), 0)# Generate a scenario pair where compensation is fixed at zero
      } 
      if (i > total_pairs*0.75) {
        replacingpair <- createScenarioPair(selectVaryingAttributes(0), 2) # Generate a scenario pair where compensation is fixed at nonzero value
      }
      #print(replacingpair)
      pairdf[i,] <- replacingpair
    }
  }
  return(pairdf)
}

replaceUntil <- function(pairdf) {
  pairdf <- checkDominatedPairs(pairdf)
  while(1 %in% pairdf$dominated){
    pairdf <- replaceDominatedPairs(pairdf)
    pairdf <- checkDominatedPairs(pairdf)
  }
  return(pairdf)
  print("Complete! There are no more dominated pairs.")
}

scenariopairdf <- replaceUntil(scenariopairdf)
```
# Balance Statistics

In this section, I'll investigate the balance of our first three attributes (participants, community, and policymakers) across compensated and uncompensated scenarios, to examine whether we're sufficiently powered to make interpretations for all combinations of these non-continous variables in contexts both with and without compensation. 

```{r}
# Create a scenario table that provides frequencies that differentiate between whether an attribute appears as A or B
abfrequencytable <- scenariopairdf %>% 
  count(Aparticipants,
        Acommunity,
        Apolicymakers,
        Bparticipants,
        Bcommunity,
        Bpolicymakers)

scenariosA <- scenariopairdf[, 1:5] %>% mutate(
  optionlabel = "A",
  choicenumber = row_number()
)

scenariosA <- scenariosA %>%
  rename(
    participants = Aparticipants,
    community = Acommunity,
    policymakers = Apolicymakers,
    compensation = Acompensation,
    researchfunding = Aresearchfunding
  )

scenariosB <- scenariopairdf[, 6:10] %>% mutate (
  optionlabel = "B",
  choicenumber = row_number()
)

scenariosB <- scenariosB %>%
  rename(
    participants = Bparticipants,
    community = Bcommunity,
    policymakers = Bpolicymakers,
    compensation = Bcompensation,
    researchfunding = Bresearchfunding
  )

# After adding labels to distinguish A and B scenarios and pair numbers, bind into one dataset
scenariosetlong <- rbind(scenariosA, scenariosB)

# Create a frequency that does not differentiate between A and B scenarios,
# Instead counting every instance of the level's occurence across both columns
orderagnosticfrequencytable <- scenariosetlong %>% count(participants,
                                                         community,
                                                         policymakers)

# This provides a frequency table of our desired levels when there is no compensation
nocompoaft <- subset(scenariosetlong, compensation == 1) %>% count(participants,
                                                         community,
                                                         policymakers)

# This provides a frequency table of our desired levels when there is nonzero compensation
compoaft <- subset(scenariosetlong, compensation != 1) %>% count(participants,
                                                         community,
                                                         policymakers)

```

# Exporting the dataset

```{r Exporting CSV}
library(openxlsx)

# Specify the string versions of the attribute levels
participantsstring = c("No results returned", "Remote", "In-person")
communitystring = c("No results returned", "Remote to community leader", "In-person meeting")
policymakersstring = c("No results returned", "Report", "Half-Day Workshop")
compensationstring = c("No additional compensation", "Compensation: 1000 TSh per participant",
                       "Compensation: 2000 TSh per participant",
                       "Compensation: 3000 TSh per participant",
                       "Compensation: 4000 TSh per participant",
                       "Compensation: 5000 TSh per participant",
                       "Compensation: 6000 TSh per participant",
                       "Compensation: 7000 TSh per participant",
                       "Compensation: 8000 TSh per participant",
                       "Compensation: 9000 TSh per participant",
                       "Compensation: 10000 TSh per participant",
                       "Compensation: 11000 TSh per participant",
                       "Compensation: 12000 TSh per participant",
                       "Compensation: 13000 TSh per participant",
                       "Compensation: 14000 TSh per participant",
                       "Compensation: 15000 TSh per participant")
researchfundingstring = c("No additional funding", "Additional research in 2 more communities", 
                          "Additional research in 4 more communities", 
                          "Additional research in 6 more communities", 
                          "Additional research in 8 more communities", 
                          "Additional research in 10 more communities",
                          "Additional research in 12 more communities",
                          "Additional research in 14 more communities",
                          "Additional research in 16 more communities",
                          "Additional research in 18 more communities",
                          "Additional research in 20 more communities")

#Specify the images that relate to each level, also "title" photos for attributes
participantsimage = c("participant1.jpeg", "participant2.jpeg", "participant3.jpeg")
communityimage = c("community1.jpeg", "community2.jpeg", "community3.jpeg")
policymakersimage = c("policy1.jpeg", "policy2.jpeg", "policy3.jpeg")
compensationimage = c("0Tsh.jpeg", "1Tsh.jpeg", "2Tsh.jpeg", "3Tsh.jpeg", "4Tsh.jpeg", "5Tsh.jpeg", "6Tsh.jpeg", "7Tsh.jpeg", "8Tsh.jpeg", "9Tsh.jpeg", "10Tsh.jpeg")
researchfundingimage = c("research0.jpeg", "research2.jpeg", "research4.jpeg", "research6.jpeg", "research8.jpeg", "research10.jpeg", "research12.jpeg", "research14.jpeg", "research16.jpeg", "research18.jpeg", "research20.jpeg")

participantstitle = "participant.jpeg"
communitytitle = "community.jpeg"
policymakerstitle = "policy.jpeg"
compensationtitle = "comp.jpeg"
researchfundingtitle = "research.jpeg"

# Add in the string versions of the attribute levels to the dataframe
stringincluded_scenariosetlong <- scenariosetlong %>% mutate(
  participants_title = participantstitle,
  participants_image = participantsimage[participants],
  participants_string = participantsstring[participants],
  community_title = communitytitle,
  community_image = communityimage[community],
  community_string = communitystring[community],
  policymakers_title = policymakerstitle,
  policymakers_image = policymakersimage[policymakers],
  policymakers_string = policymakersstring[policymakers],
  compensation_title = compensationtitle,
  compensation_image = compensationimage[compensation],
  compensation_string = compensationstring[compensation],
  researchfunding_title = researchfundingtitle,
  researchfunding_image = researchfundingimage[researchfunding],
  researchfunding_string = researchfundingstring[researchfunding]
  )



#Sort the dataframe, then add IDs in 10 row blocks
stringincluded_scenariosetlong <- stringincluded_scenariosetlong %>% arrange(choicenumber, optionlabel)
stringincluded_scenariosetlong$respondent_ID <- rep(seq(1, 450), each = 2, length.out = nrow(stringincluded_scenariosetlong))

#Reorder the columns
stringincluded_scenariosetlong <- stringincluded_scenariosetlong[,c(23,7,6,8,9,11,12,14,15,17,18,20,21)]

#Create output excel file
write.csv(stringincluded_scenariosetlong, "scenario_dataset_1.csv", row.names=FALSE)

#stringincluded_scenariosetlong$image <- NA

```



```{r Create image array output}

#For each choice set, create a stitched image with nothing in the top left, scenario 1 and scenario 2
#Next row is participants title, scenarioA participant level, scenarioB participant level
#And so on

# Number of rows and columns
num_rows <- 6
num_cols <- 3

createStitchedImage <- function(participantA, participantB, communityA, communityB, policyA, policyB, compA, compB, researchA, researchB, num) {

  # List of image filenames
  image_files <- c("blank.jpeg", "heading1.jpeg", "heading2.jpeg", 
                   "participant.jpeg", participantA, participantB, 
                   "community.jpeg", communityA, communityB, 
                   "policy.jpeg", policyA, policyB,
                   "comp.jpeg", compA, compB,
                   "research.jpeg", researchA, researchB)
  
  # Read images, handling missing files
  image_list <- lapply(image_files, function(file) {
    tryCatch(readJPEG(file), error = function(e) array(0, dim = c(100, 100, 3)))  # Default blank image if missing
  })

  # Get dimensions
  heights <- sapply(image_list, function(img) dim(img)[1])
  widths <- sapply(image_list, function(img) dim(img)[2])

  # Determine final width and height
  final_width <- max(widths)
  final_height <- max(heights)

  # Standardize image sizes
  standardized_images <- lapply(seq_along(image_list), function(i) {
    img <- image_list[[i]]
    h <- dim(img)[1]
    w <- dim(img)[2]
    blank_img <- array(1, dim = c(final_height, final_width, 3))
    start_h <- floor((final_height - h) / 2) + 1
    start_w <- floor((final_width - w) / 2) + 1
    blank_img[start_h:(start_h + h - 1), start_w:(start_w + w - 1), ] <- img
    blank_img
  })

  # Arrange images into a grid
  stitched_img <- array(0, dim = c(num_rows * final_height, num_cols * final_width, 3))
  for (r in 1:num_rows) {
    for (c in 1:num_cols) {
      idx <- (r - 1) * num_cols + c
      if (idx <= length(standardized_images)) {
        stitched_img[((r - 1) * final_height + 1):(r * final_height), 
                     ((c - 1) * final_width + 1):(c * final_width), ] <- standardized_images[[idx]]
      }
    }
  }

  # Save output
  output_filename <- paste0("stitched_output_", num, ".jpg")
  writeJPEG(stitched_img, output_filename)

  return(output_filename)
}
```


```{r Generate images for entire spreadsheet}

setwd(".")
i = 1

stringincluded_scenariosetlong$image <- NA

while(i < nrow(stringincluded_scenariosetlong)) {
    Arow <- stringincluded_scenariosetlong[i,]
    Brow <- stringincluded_scenariosetlong[i+1,]
    participantA <- stringincluded_scenariosetlong[i, 5]
    participantB <- stringincluded_scenariosetlong[i+1, 5]
    communityA <- stringincluded_scenariosetlong[i, 7]
    communityB <- stringincluded_scenariosetlong[i+1, 7]
    policyA <- stringincluded_scenariosetlong[i, 9]
    policyB <- stringincluded_scenariosetlong[i+1, 9]
    compA <- stringincluded_scenariosetlong[i, 11]
    compB <- stringincluded_scenariosetlong[i+1, 11]
    researchA <- stringincluded_scenariosetlong[i, 13]
    researchB <- stringincluded_scenariosetlong[i+1, 13]
    
    # Prints the same image for both rows that are associated with that choice
    stringincluded_scenariosetlong[i, 14] <- createStitchedImage(participantA, participantB, communityA, communityB, policyA, policyB, compA, compB, researchA, researchB, stringincluded_scenariosetlong[i, 2])
    stringincluded_scenariosetlong[i+1, 14] <- createStitchedImage(participantA, participantB, communityA, communityB, policyA, policyB, compA, compB, researchA, researchB, stringincluded_scenariosetlong[i, 2])
    i <- i + 2
}


setpredrop <- stringincluded_scenariosetlong
```

```{r Generate images for part of the spreadsheet}

setwd(".")
i = 1

stringincluded_scenariosetlong$image <- NA

while(i < nrow(stringincluded_scenariosetlong)) {
  if (i <= 3000) {
    Arow <- stringincluded_scenariosetlong[i,]
    Brow <- stringincluded_scenariosetlong[i+1,]
    participantA <- stringincluded_scenariosetlong[i, 5]
    participantB <- stringincluded_scenariosetlong[i+1, 5]
    communityA <- stringincluded_scenariosetlong[i, 7]
    communityB <- stringincluded_scenariosetlong[i+1, 7]
    policyA <- stringincluded_scenariosetlong[i, 9]
    policyB <- stringincluded_scenariosetlong[i+1, 9]
    compA <- stringincluded_scenariosetlong[i, 11]
    compB <- stringincluded_scenariosetlong[i+1, 11]
    researchA <- stringincluded_scenariosetlong[i, 13]
    researchB <- stringincluded_scenariosetlong[i+1, 13]
    
    # Prints the same image for both rows that are associated with that choice
    stringincluded_scenariosetlong[i, 14] <- createStitchedImage(participantA, participantB, communityA, communityB, policyA, policyB, compA, compB, researchA, researchB, stringincluded_scenariosetlong[i, 2])
    stringincluded_scenariosetlong[i+1, 14] <- createStitchedImage(participantA, participantB, communityA, communityB, policyA, policyB, compA, compB, researchA, researchB, stringincluded_scenariosetlong[i, 2])
  }
    i <- i + 2
}


setpredrop <- stringincluded_scenariosetlong


```



```{r}
#Had to stop image gen process, still needed the image column in name. Do not run unless stopping the image generation process early, and proceeding without the needed images. 
#gapfill <- stringincluded_scenariosetlong
gapfill <- setpredrop[!duplicated(setpredrop$choicenumber), ]
gapfill$image <- paste0("stitched_output_", 1:4500, ".jpg")

setpredrop <- gapfill

```

```{r}
#Drop the unnecessary columns and dedupe


stringincluded_scenariosetlong <- stringincluded_scenariosetlong[!duplicated(stringincluded_scenariosetlong$image), ]
#outputset <- setpredrop[,c(1,14)]

#Randomize the order of the rows
outputset <- outputset[sample(1:4500), ]

#Add back the order counter
outputset <- outputset %>%
  mutate(choicenumber = row_number())


#Create a column that counts the question number per respondent
outputset <- outputset %>%
  group_by(respondent_ID) %>%
  mutate(choicenumber2 = row_number())


#Create output excel file
write.csv(outputset, "scenario_dataset_pilot_march16.csv", row.names=FALSE)

```